%& -output-directory=C:\Users\johna\Dropbox\Chants\ -aux-directory=.\temp
% !TEX recipe = LuaLaTeX+se
%\documentclass{article}
\documentclass[10pt,parskip,paper=216mm:162mm,DIV=calc]{scrartcl} % set document class: manual at https://ctan.org/pkg/koma-script
%\usepackage{fontspec}

% Load packages:
\usepackage[osf,p]{libertine} % set font
\usepackage[autocompile]{gregoriotex} % enable Gregorio score inclusion
\usepackage[latin]{babel} % set language
\usepackage{multicol}
\usepackage[margin=1cm]{geometry}
\usepackage{scrlayer-scrpage}
%\usepackage{musixtex}

\newcommand{\myhome}{C:/Users/johna/Chant/}
\gresetgregpath{{\myhome}}

\setkomafont{section}{\normalfont\centering\huge\scshape} % section heading style
\setkomafont{subsection}{\normalfont\centering\Large\bfseries} % section heading style
\setkomafont{subsubsection}{\normalfont\centering\small\scshape} % section heading style
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\setkomafont{pagehead}{\scshape}
\automark[section]{section}
\automark*[subsection]{subsection}

%\lohead[\thesubsection]
%{\thesubsection}
%\rohead[\thesubsection]
%{\thesubsection}
\pagestyle{scrheadings}

\RedeclareSectionCommand[
    runin=true,
    afterindent=false,
    beforeskip=0.75ex plus 1ex minus .2ex,
    afterskip=3pt]{paragraph}

% Set the space around the initial:
% See http://gregorio-project.github.io/gregoriotex/details.html for more details and options
\grechangedim{beforeinitialshift}{2.2mm}{scalable}
\grechangedim{afterinitialshift}{2.2mm}{scalable}

% Set the initial font (change 43 for a larger size):
%\grechangestyle{initial}{\fontsize{43}{43}\selectfont}%

% Make staff lines red; remove for black:
%\gresetlinecolor{gregoriocolor}

% Use the "commentary" field of the score in the top right corner:
\gresetheadercapture{commentary}{grecommentary}{string}

% Format annotation above initial
\grechangestyle{annotation}{\small\bfseries}

\begin{document}
\subsection{12th Week in Ordinary Time}

\paragraph{Entrance Antiphon \& Introit} \emph{Cf. Ps 28 (27):8-9}
The Lord is the strength of his people,
a saving refuge for the one he has anointed.
Save your people, Lord, and bless your heritage,
and govern them for ever.

\begin{multicols}{3}
   \paragraph{Gradual}~
   \small
   \textbf{Convertere}\\
   \emph{Ps. 89:13,1} Turn back, O Lord! How long? 
   Show pity to your servants.
   \Vbar O Lord, you have been our refuge, 
   from generation to generation.

   \columnbreak
   \textbf{Beata gens} \emph{Mon. Year I}\\
   \emph{Ps. 32:12,6} Blessed the nation whose God is the Lord, 
   the people he has chosen as his heritage.
   \Vbar By the word of the Lord the heavens were made, 
   by the breath of his mouth all their host.
   
   \columnbreak
   \textbf{Respice, Domine} \emph{Sat. Year II}\\
   \emph{Ps. 73: 20, 19 \Vbar 22, 23}
   Look to your covenant,
   do not forget forever the life of your afflicted.
   \Vbar Arise, O God, and defend your cause!
   Remember the reproach of your servants.

\end{multicols}

\paragraph{Gradual Alleluia} \emph{Ps 30:2-3} In you, O Lord, I take refuge. 
Let me never be put to shame. 
In your justice, set me free; 
incline your ear to me, and speedily rescue me. 

\paragraph{Offertory Chant} \emph{Cf. Ps. 16, 5. 6. 7}
I kept my steps firmly in your paths. 
My feet have never faltered. 
Turn your ear to me; hear my words. 
Display your merciful love, 
you who deliver from their foes 
those who trust in your right hand. 


\paragraph{Communion Antiphon} \emph{Ps 145 (144): 15}
The eyes of all look to you, Lord,
and you give them their food in due season.

Or, \emph{Jn 10: 11, 15}
I am the Good Shepherd,
and I lay down my life for my sheep, says the Lord.

\begin{multicols}{3}
   \paragraph{Communion chants}~\\
   \small
    {\bfseries Circuibo}\\
    \emph{Ps. 26:6}
    I shall offer within his tent
   sacrifices full of exultation.
   I will sing and make music for the Lord. 
   \columnbreak

   {\bfseries Quod dico vobis}
   \emph{Sun. Year A}\\
   \emph{Mt. 10:27}
   What I say to you in the darkness, speak in the light, says the Lord.
   What you hear whispered, proclaim on the housetops.
   \columnbreak

   {\bfseries Qui vult venire}
   \emph{Sun. Year C}\\
   \emph{Mt 16:24}
   Whoever wishes to come after me, must deny himself,
   take up his cross, and follow me.
\end{multicols}

\filbreak
\greannotation{In. II}
\gregorioscore{Introitus/dominus-fortitudo/english.gabc}

\filbreak
\greannotation{Of. IV}
\gregorioscore{Offertorium/perfice-gressus/english.gabc}

\filbreak
\greannotation{Co. VI}
\gregorioscore{Communio/circuibo/english.gabc}
\gresetinitiallines{0}
\gabcsnippet{
(c2)The(fg) eyes(gf) of(gh) all(h) <i>look</i>(g) <b>to</b>(i) you,(h) <b>Lord</b>(g.) (:)<i>and</i>(f) <i>you</i>(gh) <i>give</i>(h) <b>them</b>(hj) their(g) <i>food</i>(fd) <i>in</i>(f) <i>due</i>(g) <b>sea</b>(g)son.(f.) (::)
}
\gresetinitiallines{1}

\filbreak
\greannotation{Co. IV}
\gregorioscore{Communio/quod-dico-vobis/english.gabc}
\gresetinitiallines{0}
\gabcsnippet{
(c4)The(hg) eyes(gh) of(h) <i>all</i>(hg) <i>look</i>(gi) <i>to</i>(i) <b>you</b>,(hi) Lord,(h.) * (:) and(hg) you(gh) give(h) them(h) their(h) food(h) <i>in</i>(gf) <i>due</i>(gh) <i>sea</i>(g)<i>son</i>.(e.) (::)
}
\gresetinitiallines{1}

\filbreak
\greannotation{Co. I}
\gregorioscore{Communio/qui-vult-venire/english.gabc}
\gresetinitiallines{0}
\gabcsnippet{
(c4)The(f) eyes(gh) of(h) all(h) <i>look</i>(hj) <i>to</i>(h) <i>you</i>,(hg) <i>Lord</i>,(gh..) * (:) and(gf) you(gh) give(h) them(h) their(h) <i>food</i>(hjh) <i>in</i>(g) <i>due</i>(f) <i>sea</i>(fff)<i>son</i>.(d.) (::)
}
\gresetinitiallines{1}


\subsubsection{Year I: Thursday}

\greannotation{Ant.}
\greannotation{5}
\grecommentary{106:1b-2, 3-4a, 4b-5}
% Give thanks to the Lord, for he is good.
%\gabcsnippet{(c3)Give thanks to the Lord, for he is good.}

\begin{multicols}{2}
\begin{itemize}
    \small
\item Give thanks to the LORD, for he is good,\\
   for his mercy endures forever.\\
Who can tell the mighty deeds of the LORD,\\
   or proclaim all his praises?

\item Blessed are they who observe what is right, \\
   who do always what is just. \\
Remember us, O LORD, as you favor your people.


\item Visit me with your saving help, \\
that I may see the prosperity of your chosen ones, \\
   rejoice in the joy of your people, \\
   and glory with your inheritance.

\end{itemize}

\end{multicols}

%\greannotation{Alle}
%\greannotation{VI}
%\gregorioscore{alleluia-no/you-have-received-a-spirit/english.gabc}
\paragraph{Alleluia} Whoever loves me will keep my word,
and my Father will love him
and he will come to him.



\end{document}