\item that he may judge your \textbf{peo}ple in \textbf{just}ice,~\mediant
 and your \textbf{poor} in right \textbf{judg}ment.

\item May the mountains bring forth \textbf{peace} for the \textbf{peo}ple,~\mediant
 and the hills bear \textbf{peace} in up\textbf{right}ness.

\item May he defend the poor of the peo-\emph{ple},~\flex
 and save the children \textbf{of} the \textbf{nee}dy,~\mediant
 and \textbf{crush} the op\textbf{pres}sor.

\item He shall endure like the \textbf{sun} and \textbf{the} moon~\mediant
 through all \textbf{ge}ne\textbf{ra}tions.

\item He shall descend like \textbf{rain} on the \textbf{mea}dow,~\mediant
 like showers that \textbf{wa}ter \textbf{the} earth.

\item In his days \textbf{just}ice shall \textbf{flour}ish,~\mediant
 and great peace till the \textbf{moon} is \textbf{no} more.

\item He shall rule \textbf{from} sea \textbf{to} sea,~\mediant
 from the River to the \textbf{bounds} of \textbf{the} earth.

\item Let the desert dwellers fall \textbf{be}fo\textbf{re} him,~\mediant
 and his enemies \textbf{l}ick \textbf{the} dust.

\item The kings of Tarshish \textbf{and} the \textbf{is}lands~\mediant
 shall pay \textbf{him} tri\textbf{bu}te.

\item The kings of \textbf{She}ba and \textbf{Se}ba~\mediant
 \textbf{shall} bring \textbf{him} gifts.

\item Before him all kings shall \textbf{fall} pro\textbf{stra}te,~\mediant
 all nati\textbf{ons} shall \textbf{ser}ve him.

\item For he shall rescue the nee\textbf{dy} when \textbf{the}y cry,~\mediant
 the poor who have no \textbf{o}ne \textbf{to} help.

\item He will have pity on the weak and \textbf{the} ne\textbf{e}dy,~\mediant
 and save the lives of \textbf{the} ne\textbf{e}dy.

\item From oppression and violence he redeems \textbf{the}ir \textbf{li}fe;~\mediant
 to him their \textbf{blo}od is \textbf{de}ar.

\item Long may he live, and the gold of \textbf{She}ba be \textbf{gi}ven him.

\item They shall pray for him witho\textbf{ut} ce\textbf{a}sing,~\mediant
 and bless \textbf{him} all \textbf{the} day.

\item May grain be abun\textbf{dant} in \textbf{the} land,~\mediant
 waving to the peaks of the \textbf{mo}un\textbf{ta}ins.

\item May its fruit rustle like Lebanon;~\flex
 may the people flourish in \textbf{the} ci\textbf{ti}es~\mediant
 like grass \textbf{on} the \textbf{e}arth.

\item May his name endu\textbf{re} fo\textbf{re}ver,~\mediant
 his name continue \textbf{li}ke \textbf{the} sun.

\item Every tribe shall \textbf{be} blest \textbf{in} him,~\mediant
 all nations shall \textbf{call} him \textbf{bles}sed.

\item Blest be the Lord, \textbf{God} of \textbf{Is}rael,~\mediant
 who alone \textbf{w}orks \textbf{won}ders,

\item ever blest his glori\textbf{o}us \textbf{na}me.~\mediant
 Let his glory fill the earth. \textbf{A}men! \textbf{A}men!