\item O God, give your judgment to the king, *
to a king's son your justice, 
\item that he may judge your people in justice, *
and your poor in right judgment. 
\item May the mountains bring forth peace for the people, *
and the hills bear peace in uprightness. 
\item May he defend the poor of the people, +
and save the children of the needy, *
and crush the oppressor. 
\item He shall endure like the sun and the moon *
through all generations. 
\item He shall descend like rain on the meadow, *
like showers that water the earth. 
\item In his days justice shall flourish, *
and great peace till the moon is no more. 
\item He shall rule from sea to sea, *
from the River to the bounds of the earth. 
\item Let the desert dwellers fall before him, *
and his enemies lick the dust. 
\item The kings of Tarshish and the islands *
shall pay him tribute. //
The kings of Sheba and Seba *
shall bring him gifts. 
\item Before him all kings shall fall prostrate, *
all nations shall serve him. 
\item For he shall rescue the needy when they cry, *
the poor who have no one to help. 
\item He will have pity on the weak and the needy, *
and save the lives of the needy. 
\item From oppression and violence he redeems their life; *
to him their blood is dear. 
\item Long may he live, and the gold of Sheba be given him. \\
They shall pray for him without ceasing, *
and bless him all the day. 
\item May grain be abundant in the land, *
waving to the peaks of the mountains. \\
May its fruit rustle like Lebanon; +
may the people flourish in the cities *
like grass on the earth. 
\item May his name endure forever, *
his name continue like the sun. \\
Every tribe shall be blest in him, *
all nations shall call him blessed. 
\item Blest be the Lord, God of Israel, *
who alone works wonders, 
\item ever blest his glorious name. *
Let his glory fill the earth. Amen! Amen! 

