% !TEX root = II-vespers.tex
% !TEX recipe = LuaLaTeX+se
%\documentclass{article}
\documentclass[parskip]{scrartcl} % set document class: manual at https://ctan.org/pkg/koma-script
%\usepackage{fontspec}

% Load packages:
\usepackage[osf,p]{libertine} % set font
\usepackage[autocompile]{gregoriotex} % enable Gregorio score inclusion
\usepackage[latin]{babel} % set language
\usepackage{multicol}
\usepackage[margin=3cm]{geometry}
\usepackage{scrlayer-scrpage}

\newenvironment{verses}[1][2]{
\begin{multicols}{#1}
\footnotesize
}{
\end{multicols}}

\setkomafont{section}{\normalfont\centering\huge\scshape} % section heading style
\setkomafont{subsection}{\normalfont\centering\Large\scshape} % section heading style
\setkomafont{subsubsection}{\normalfont\centering\small\scshape} % section heading style
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\setkomafont{pagehead}{\scshape}
%\automark[section]{section}
%\automark*[subsection]{subsection}

%\lohead[\thesection]
%{\thesection}
%\rohead[\thesubsection]
%{\thesubsection}
%\pagestyle{scrheadings}

\def\translation{NABRE}

% Set the space around the initial:
% See http://gregorio-project.github.io/gregoriotex/details.html for more details and options
\grechangedim{beforeinitialshift}{2.2mm}{scalable}
\grechangedim{afterinitialshift}{2.2mm}{scalable}

% Set the initial font (change 43 for a larger size):
%\grechangestyle{initial}{\fontsize{43}{43}\selectfont}%

% Make staff lines red; remove for black:
%\gresetlinecolor{gregoriocolor}

% Use the "commentary" field of the score in the top right corner:
\gresetheadercapture{commentary}{grecommentary}{string}

% Format annotation above initial
\grechangestyle{annotation}{\small\bfseries}

\begin{document}

\thispagestyle{plain}
\section{Office of Second Vespers}
\subsection{Sunday, Psalter Week III in Ordinary Time}
\begin{center}
    \emph{For the third week in the four-week psalter cycle, not just the 3rd Sunday in Ordinary Time.}

    \emph{The Nth Sunday in Ordinary Time is in Psalter week III if N divided by 4 has a remainder of three.}

    \emph{This Office is incomplete - each Sunday has proper antiphons at Magnificat and Benedictus.}
\end{center}

\subsection{Introduction}
\input{C:/Users/johna/Chant/Communes/deus-in-adjutorium/festivus.gtex}
\begin{center}
    \emph{Oh God, come to my assistance. --\textbf{LORD, make haste to help me.}\\
    Glory be to the Father, and to the Son, and to the Holy Spirit.
    --\textbf{As it was in the beginning, is now, and ever shall be, world with out end. Amen. Alleluia.}}
    %\greseparator{3}{10}
\end{center}

% Lucis creator (LHymn 188)
\subsubsection*{Hymn: ``Lucis Creator'' \hfill
{\small\itshape Attr. St. Gregory the Great, ca 540-604; tr. © 2023 ICEL}}
\subsubsection{In summer time:}
\input{C:/Users/johna/Chant/hymns/lucis-creator/in-aestate_v1-ICEL.gtex}
\subsubsection{In winter time:}
\input{C:/Users/johna/Chant/hymns/lucis-creator/in-hieme_v1-ICEL.gtex}
\begin{multicols*}{2}
    \input{C:/Users/johna/Chant/hymns/lucis-creator/verses-ICEL.tex}    
\end{multicols*}


\subsection{Psalmody}
%% FIRST PSALM %%
\input{C:/Users/johna/Chant/Antiphona/dixit-dominus/dbl.tex}

\vspace*{-15pt}
\subsubsection{2nd Antiphon}

%% SECOND PSALM %%
\input{C:/Users/johna/Chant/Antiphona/fidelia-omnia/dbl.tex}


%% NT CANTICLE %%
\subsubsection*{Canticle: The Wedding of the Lamb \hfill ARII 10; (Solesmes)}
\input{C:/Users/johna/Chant/Canticum/salus-et-gloria/english.gtex}


\subsection{Reading \hfill 1 Peter 1:3-5}
Probably proper (see iBreviary)

\subsubsection{Responsory}
\input{C:/Users/johna/Chant/Resp-breve/benedictus-es-domine/english.gtex}

\subsection{Gospel Canticle}
PROPER TO EACH SUNDAY. See the OCO for this week's.
%\input{C:/Users/johna/Chant/Antiphona/sinite-parvulos/dbl.tex}

\subsection{Intercessions}
\begin{multicols}{2}
    \small
Proper (see iBreviary)
\end{multicols}

\subsubsection{Our Father}
\input{C:/Users/johna/Chant/Communes/pater-noster/English-C.gtex}

%\gresetinitiallines{0} 
%\gresetinitiallines{1} 

\subsubsection{Prayer}
    Proper (see iBreviary)

\subsubsection{Dismissal}
\begin{multicols}{2}
    \small
\emph{If a priest or deacon presides:}

The Lord be with you.\\
— \textbf{And with your spirit.}

May almighty God bless you,\\
the Father, and the Son, and the Holy Spirit.\\
— \textbf{Amen}.

Go in peace.\\
— \textbf{Thanks be to God.}

\columnbreak

\emph{In the absence of a priest or deacon and in individual recitation, Evening Prayer concludes:}

May the Lord + bless us,\\
protect us from all evil\\
and bring us to everlasting life.
— \textbf{Amen}.
\end{multicols}


\end{document}