% !TEX recipe = LuaLaTeX+se


%\documentclass[handout]{loth}


\documentclass[lectionary,missingscore=warn,nogloria]{loth} % Show todos
%\documentclass[lectionary,missingscore=silent]{loth}   % choir behavior anyway

%\documentclass[choir]{loth}                   % choir behavior anyway

%\documentclass[handout,intro=text]{loth}      % Force compact intro for page-fitting
%\documentclass[handout,intro=graphic]{loth}   % Force graphic intro explicitly

%\documentclass[pamphlet,intro=text,textonly=true]{loth}     % pamphlet + compact intro
%\documentclass[fontsize=12pt,pamphlet,intro=graphic,margin=1cm,textonly=false]{loth}     % pamphlet + compact intro

\begin{document}

\thispagestyle{plain}
\section{Holy Thursday}

\subsection{At Matins}

\subsubsection{First Nocturn}

\emph{Pre-1955: Pater noster, Ave Maria, Credo, in silence.}

\paragraph{Psalm 69[68]}
\psalm{zelus-domus}{69}{8c}{1-0-1-2}

\paragraph{Psalm 70[69]}
\psalm{avertantur-retrorsum}{70}{8c}{1-0-1-2}

\paragraph{Psalm 71[70]}
\psalm{deus-meus-eripe}{71}{8c}{1-0-1-2}

\gresetinitiallines{0}
\gabcsnippet{(c4) <sp>V/</sp>. Let(h) them(h) be(h) turned(h) back(h) and(h) put(i) to(h) shame.(g.) (::)
<sp>V/</sp>. That(h) in(h)tend(h) e(h)vil(i) a(h)gainst(g.) me.(g.) (::)}
\gresetinitiallines{1}

Our Father. \emph{In silence.}

\lesson{Lamentations-Thurs-1-Silos-NAB}{Lamentations 1:1-5}
\gregorioscore{Responsum/in-monte-oliveti/english.gabc}

\lesson{Lamentations-Thurs-2-Silos-NAB}{Lamentations 1:6-9}
\gregorioscore{Responsum/tristis-est/english.gabc}

\lesson{Lamentations-Thurs-3-Silos-NAB}{Lamentations 1:10-14}
\gregorioscore{Responsum/ecce-vidimus/english.gabc}


\subsubsection{Second Nocturn}

\paragraph{Psalm 72[71]}
\psalm{liberavit-dominus}{72}{7c}{2-0-2-0}

\paragraph{Psalm 73[72]}
\psalm{cogitaverunt-impii}{73}{8c}{1-0-1-2}

\paragraph{Psalm 74[73]}
\psalm{exsurge-domine}{74}{1g}{2-0-1-2}

\gresetinitiallines{0}
\gabcsnippet{
(c4)  <sp>V/</sp>. My(h) God,(h) free(h) me(h) from(h) the(h) hand(h) of(i) the(h) wick(g)ed,(g.) * (::)
 <sp>R/</sp>. from(h) the(h) grip(h) of(h) the(h) un(h)just,(h) of(h) the(i) op(h)pres(g.)sor.(g.) (::)}
\gresetinitiallines{1}

Our Father. \emph{In silence.}

\lesson{Thurs2-1}{Commentary of St Augustine on Psalm 54}
\gregorioscore{Responsum/amicus-meus/english.gabc}

\lesson{Thurs2-2}{}
\gregorioscore{Responsum/judas-mercator/english.gabc}

\lesson{Thurs2-3}{}
\gregorioscore{Responsum/unus-ex-discipulis/english.gabc}



\subsubsection{Third Nocturn}

\paragraph{Psalm 75[74]}
\psalm{dixi-iniquis}{75}{7c}{2-0-2-0}

\paragraph{Psalm 76[75]}
\psalm{terra-tremuit}{76}{8c}{1-0-1-2}

\paragraph{Psalm 77[76]}
\psalm{in-die-tribulationis}{77}{7a}{2-0-2-0}

\gresetinitiallines{0}
\gabcsnippet{
(c4) <sp>R/</sp>. A(g)rise,(h) O(g) Lord.(f.) (::)
<sp>V/</sp>. And(g) judge(h) my(g) cause.(f.::)}
\gresetinitiallines{1}

Our Father. \emph{In silence.}

\lesson{Thurs3-1}{1 Corinthians 11:17-22}
\gregorioscore{Responsum/eram-quasi/english.gabc}

\lesson{Thurs3-2}{1 Corinthians 11:23-26}
\gregorioscore{Responsum/una-hora/english.gabc}

\lesson{Thurs3-3}{1 Corinthians 11:27-34}
\gregorioscore{Responsum/seniores-populi/english.gabc}


\subsection{At Lauds}
\setcounter{antcnt}{1}

\psalm{justificeris-domine}{51}{8g}
\psalm{dominus-tamquam-ovis}{90}{2d}
\psalm{contritum-est}{36}{7c}
\psalm{exhortatus-es}{Exod-15}{4alta}
\psalm{oblatus-est}{147a}{2d}
\gresetinitiallines{0}
%\gabcsnippet{} %TODO versicle
\gresetinitiallines{1}
\psalm{traditor-autem}{Benedictus}{1g-sol}{1-3-1-2}

\gregorioscore{Gradual/christus-factus-est/english.gabc}

\setcounter{antcnt}{1}
\setcounter{lessoncnt}{1}
\section{Good Friday}

\subsection{At Matins}

\subsubsection{First Nocturn}

\emph{Pre-1955: Pater noster, Ave Maria, Credo, in silence.}

\paragraph{Psalm 2}
\psalm{astiterunt-reges-terrae}{2}{x}

\paragraph{Psalm 21}
\psalm{diviserunt-sibi}{21}{x}

\paragraph{Psalm 26}
\psalm{insurrexerunt-in-me}{26}{x}

\gresetinitiallines{0}
%\gabcsnippet{} %TODO versicle: Diviserunt sibi
\gresetinitiallines{1}

Our Father. \emph{In silence.}

\subsubsection{First Reading: Lamentations}
\gregorioscore{Lectionis/Lamentations-Fri-1-Silos-NAB.gabc}
\gregorioscore{Responsum/omnes-amici-mei/english.gabc}

\subsubsection{Second Reading: Lamentations}
\gregorioscore{Lectionis/Lamentations-Fri-2-Toledo-NAB.gabc}
\gregorioscore{Responsum/velum-templi/english.gabc}

\subsubsection{Third Reading: Lamentations}
\gregorioscore{Lectionis/Lamentations-Fri-3-Leon-NAB.gabc}
\gregorioscore{Responsum/vinea-mea/english.gabc}


\subsubsection{Second Nocturn}

\paragraph{Psalm 37}
\psalm{vim-faciebant}{37}{x}

\paragraph{Psalm 39}
\psalm{confundantur}{39}{x}

\paragraph{Psalm 53}
\psalm{alieni-insurrexerunt}{53}{x}

\gresetinitiallines{0}
%\gabcsnippet{} %TODO versicle: Insurrexerunt in me
\gresetinitiallines{1}

Our Father. \emph{In silence.}

\lesson{Fri2-1}{Commentary of St Augustine on Psalm 63}
\gregorioscore{Responsum/tamquam-ad-latronem/english.gabc}

\lesson{Fri2-2}{}
\gregorioscore{Responsum/tenebrae-factae-sunt/english.gabc}

\lesson{Fri2-3}{}
\gregorioscore{Responsum/animam-meam-dilectam/english.gabc}


\subsubsection{Third Nocturn}

\paragraph{Psalm 58}
\psalm{ab-insurgentibus}{58}{x}

\paragraph{Psalm 87}
\psalm{longe-fecisti}{87}{x}

\paragraph{Psalm 93}
\psalm{captabunt}{93}{x}

\gresetinitiallines{0}
%\gabcsnippet{} %TODO versicle: Locuti sunt adversum me
\gresetinitiallines{1}

Our Father. \emph{In silence.}

\lesson{Fri3-1}{Hebrews 4:11--15}
\gregorioscore{Responsum/tradiderunt-me/english.gabc}

\lesson{Fri3-2}{Hebrews 4:16--5:3}
\gregorioscore{Responsum/jesum-tradidit/english.gabc}

\lesson{Fri3-3}{Hebrews 5:4--10}
\gregorioscore{Responsum/caligaverunt-oculi/english.gabc}


\subsection{At Lauds}
\setcounter{antcnt}{1}

\psalm{proprio-filio}{50}{x}
\psalm{anxiatus-est}{142}{x}
\psalm{ait-latro-ad-latronem}{84}{x}
\psalm{dum-conturbata}{Hab-3}{x}
\psalm{memento-mei}{147}{x}
\gresetinitiallines{0}
%\gabcsnippet{} %TODO versicle: Collocavit me
\gresetinitiallines{1}
\psalm{posuerunt-super-caput}{Benedictus}{x}

\gregorioscore{Gradual/christus-factus-est/english.gabc}

\setcounter{antcnt}{1}
\setcounter{lessoncnt}{1}
\section{Holy Saturday}

\subsection{At Matins}

\subsubsection{First Nocturn}

\emph{Pre-1955: Pater noster, Ave Maria, Credo, in silence.}

\paragraph{Psalm 4}
\psalm{in-pace}{4}{x}

\paragraph{Psalm 14}
\psalm{habitabit-in-tabernaculo}{14}{x}

\paragraph{Psalm 15}
\psalm{caro-mea}{15}{x}

\gresetinitiallines{0}
%\gabcsnippet{} %TODO versicle: In pace in idipsum
\gresetinitiallines{1}

Our Father. \emph{In silence.}

\subsubsection{First Reading: Lamentations}
\gregorioscore{Lectionis/Lamentations-Sat-1-Silos-NAB.gabc}
\gregorioscore{Responsum/sicut-ovis/english.gabc}

\subsubsection{Second Reading: Lamentations}
\gregorioscore{Lectionis/Lamentations-Sat-2-Leon-NAB.gabc}
\gregorioscore{Responsum/jerusalem-surge/english.gabc}

\subsubsection{Third Reading: Lamentations}
\gregorioscore{Lectionis/Lamentations-Sat-3-adlib-NAB.gabc}
\gregorioscore{Responsum/plange-quasi-virgo/english.gabc}


\subsubsection{Second Nocturn}

\paragraph{Psalm 23}
\psalm{elevamini}{23}{x}

\paragraph{Psalm 26}
\psalm{credo-videre}{26}{x}

\paragraph{Psalm 29}
\psalm{domine-abstraxisti}{29}{x}

\gresetinitiallines{0}
%\gabcsnippet{} %TODO versicle: Tu autem
\gresetinitiallines{1}

Our Father. \emph{In silence.}

\lesson{Sat2-1}{}
\gregorioscore{Responsum/recessit-pastor/english.gabc}

\lesson{Sat2-2}{}
\gregorioscore{Responsum/o-vos-omnes/english.gabc}

\lesson{Sat2-3}{}
\gregorioscore{Responsum/ecce-quomodo/english.gabc}


\subsubsection{Third Nocturn}

\paragraph{Psalm 53}
\psalm{deus-adjuvat-me}{53}{x}

\paragraph{Psalm 75}
\psalm{in-pace-factus}{75}{x}

\paragraph{Psalm 87}
\psalm{factus-sum}{87}{x}

\gresetinitiallines{0}
%\gabcsnippet{} %TODO versicle: In pace factus est
\gresetinitiallines{1}

Our Father. \emph{In silence.}

\lesson{Sat3-1}{Hebrews 9:11--14}
\gregorioscore{Responsum/astiterunt-reges-terrae/english.gabc}

\lesson{Sat3-2}{Hebrews 9:15--18}
\gregorioscore{Responsum/aestimatus-sum/english.gabc}

\lesson{Sat3-3}{Hebrews 9:19--22}
\gregorioscore{Responsum/sepulto-domino/english.gabc}


\subsection{At Lauds}
\setcounter{antcnt}{1}

\psalm{o-mors}{50}{x}
\psalm{plangent-eum}{91}{x}
\psalm{attendite}{63}{x}
\psalm{a-porta-inferi}{Isa-38}{x}
\psalm{o-vos-omnes-qui-transitis}{150}{x}
\gresetinitiallines{0}
%\gabcsnippet{} %TODO versicle: Caro mea
\gresetinitiallines{1}
\psalm{mulieres-sedentes}{Benedictus}{x}

\gregorioscore{Gradual/christus-factus-est/english.gabc}

\end{document}