% !TEX root = 8-OT-C-VII.tex
% !TEX recipe = LuaLaTeX+se
%\documentclass{article}
\documentclass[paper=letter,parskip]{scrartcl} % set document class: manual at https://ctan.org/pkg/koma-script
%\usepackage{fontspec}

% Load packages:
\usepackage[osf,p]{libertine} % set font
\usepackage[autocompile]{gregoriotex} % enable Gregorio score inclusion
\usepackage[latin]{babel} % set language
\usepackage{multicol}
\usepackage[margin=2cm]{geometry}
\usepackage{scrlayer-scrpage}
\usepackage{xargs}

\newcommand{\myhome}{C:/Users/johna/Chant/}
\gresetgregpath{{\myhome}}

\setkomafont{section}{\normalfont\centering\huge\scshape\bfseries} % section heading style
\setkomafont{subsection}{\normalfont\centering\Large\scshape} % section heading style
\setkomafont{subsubsection}{\normalfont\centering\small\scshape} % section heading style
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\setkomafont{pagehead}{\scshape}
%\automark[section]{section}
%\automark*[subsection]{subsection}

%spacing before and after headers
\RedeclareSectionCommand[
  %runin=false,
  afterindent=false,
  beforeskip=.25\baselineskip,
  afterskip=.15\baselineskip]{subsubsection}
\RedeclareSectionCommand[
%runin=false,
    afterindent=false,
    beforeskip=.15\baselineskip,
    afterskip=.05\baselineskip]{subsection}
\RedeclareSectionCommand[
    %runin=false,
    afterindent=false,
    beforeskip=.25\baselineskip,
    afterskip=.15\baselineskip]{section}
\RedeclareSectionCommand[
    runin=false,
    afterindent=false,
    beforeskip=3.25ex plus 1ex minus .2ex,
    afterskip=3pt]{paragraph}
%\lohead[\thesection]
%{\thesection}
%\rohead[\thesubsection]
%{\thesubsection}
%\pagestyle{scrheadings}

\usepackage{soul}
\sethlcolor{white}
\let\oldhl\hl
\renewcommand{\hl}[1]{\ifchoir \oldhl{#1} \else #1 \fi}


\newif\iflect
\lectfalse

\newif\ifchoir
\choirfalse

\iflect\choirtrue\fi


% Set the space around the initial:
% See http://gregorio-project.github.io/gregoriotex/details.html for more details and options
\grechangedim{beforeinitialshift}{2.2mm}{scalable}
\grechangedim{afterinitialshift}{2.2mm}{scalable}
 
% Set the initial font (change 43 for a larger size):
%\grechangestyle{initial}{\fontsize{43}{43}\selectfont}%

% Make staff lines red; remove for black:
%\gresetlinecolor{gregoriocolor}

% Use the "commentary" field of the score in the top right corner:
\gresetheadercapture{commentary}{grecommentary}{string}
\grechangedim{commentaryseparation}{0.15mm}{scalable}

% Format annotation above initial
\grechangestyle{annotation}{\small\bfseries}


\newcommand{\hymn}[3]{
\subsubsection*{Hymn: ``#2'' \hfill
{\small\itshape #3}}
\ifchoir
\gregorioscore{hymns/#1/english.gabc}
\else
\gregorioscore{hymns/#1/english_v1.gabc}
    \begin{multicols}{3}
        \small
        \input{\myhome/hymns/#1/verses.tex}
\end{multicols}
\fi}

\newcommand{\introd}[1]{
    %\subsection{Introduction}
    \marginpar{\small\scshape Stand}
    \ifchoir
    \gregorioscore{Communes/deus-in-adjutorium/#1}
    \else
    \begin{center}
        \emph{Oh God, come to my assistance. --\textbf{LORD, make haste to help me.}\\
        Glory be to the Father, and to the Son, and to the Holy Spirit.
        --\textbf{As it was in the beginning, is now, and ever shall be, world with out end. Amen. Alleluia.}}
        %\greseparator{3}{30}
    \end{center}
    \fi
}

\newcommandx{\psalm}[5][5=solesmes]{
    \gregorioscore{Antiphona/#1/#5.gabc}
    \gresetinitiallines{0}
    \ifchoir
    \gregorioscore{Psalms/#2/#3.gabc}
    \begin{multicols}{2}
        \small
        \input{\myhome/Psalms/#2/#4.tex}

        \input{\myhome/Psalms/GloriaPatri/#4.tex}
    \end{multicols}
    \else
    \begin{multicols}{2}
        \small
        \input{\myhome/Psalms/#2/all.tex}
    \end{multicols}
    \fi
    \gregorioscore{Antiphona/#1/english.gabc}
    \gresetinitiallines{1}
}

\newcommandx{\responsory}[2][2=english]{
    \subsubsection{Responsory}
    \ifchoir
\gregorioscore{Resp-breve/#1/#2-extended.gtex}
\else
\gregorioscore{Resp-breve/#1/#2.gtex}
\fi
}

\begin{document}

\thispagestyle{plain}
\section{Vespers II: Third Sunday of Easter, 2025 \iflect LECTIONARY \else\ifchoir CHOIR\fi\fi}
\iflect
\else
\ifchoir
\else
%\begin{center}
%    \emph{Feast of the Presentation of the Lord}
    %\emph{Prepared by Dr. J. Costanzo}
    %
    %    \greseparator{3}{30}
%\end{center}
%\vspace{-0.5cm}
\fi
\fi

\introd{solemnis}

\vspace{-15pt}
\hymn{ad-coenam}{Ad cenam Agni providi}{attr. Saint Nicetas of Remesiana, ca. 335-414, © 2023 ICEL}

\vspace{-15pt}
%\subsection{Psalmody}
\marginpar{\small\scshape Sit}
\vspace{-15pt}
%% FIRST PSALM %%
\paragraph{Psalm 110[109]}
\greannotation{Ant. 1}
\greannotation{1g}
%\grecommentary{Ps. 110}
\psalm{purgationem-peccatorum}{110}{1g}{2-0-1-2}

%% SECOND PSALM %%
\paragraph{Psalm 111[110]}
\greannotation{Ant. 2}
\greannotation{8g}
%\grecommentary{Ps. 130}
\psalm{redemptionem-misit}{111}{8g}{1-0-1-2}[verona]


%% NT CANTICLE %%
% \paragraph{Canticle: }
% \greannotation{Ant. 3}
% \greannotation{5a}
% %\grecommentary{1 Peter 2:21-24}
% \psalm{alleluia-audivi}{1Pet2-21}{5a}{1-0-2-0}[verona]
\paragraph{Canticle: Wedding Feast of the Lamb}
\gregorioscore{Antiphona/alleluia-audivi/solesmes-alleluia.gabc}
\ifchoir
\greannotation{Cant.}
\greannotation{8}
\gregorioscore{Canticum/salus-et-gloria/english-TP-nolinebreak}
\else
\begin{multicols}{2}
    \small
    \input{Canticum/salus-et-gloria/text.tex}    
\end{multicols}
\fi
\gresetinitiallines{0}
\gregorioscore{Antiphona/alleluia-audivi/english.gabc}
\gresetinitiallines{1}


\subsection{Reading: Hebrews 10:12-14}
\iflect
\gresetinitiallines{0}
\gabcsnippet{
    (c3) Je(h)sus(h) off(h)ered(h) o(h)ne(h) sa(h)cri(h)fice(h) for(h) sins(h) and(h) took(h) his(h) seat(h) for(h)ev(h)er(h) at(h) the(h) right(h) <i>hand</i>(g) <i>of</i>(f) <i>God</i>;(h.) (;) now(h) he(h) waits(h) un(h)til(h) his(h) e(h)ne(h)mies(h) are(h) placed(h) be(h)neath(h) <b>his</b>(f) feet.(ef..) (:) By(h) one(h) of(h)fer(h)ing(h) he(h) has(h) fo(h)re(h)ver(h) per(h)fec(h)ted(h) those(h) who(h) are(h) be(h)ing(h) sanc(h)<b>ti</b>(f)fied.(ef..) (::)}
\gresetinitiallines{1}
\else
Jesus offered one sacrifice for sins and took his seat forever at the right hand of God; now he waits until his enemies are placed beneath his feet. By one offering he has forever perfected those who are being sanctified.
\fi

\greannotation{Resp.}
\greannotation{6}
\responsory{surrexit-dominus-vere-solemnis}


\subsection{Gospel Canticle}
\marginpar{\small\scshape Stand}
\grechangedim{commentaryraise}{3.5mm}{scalable}
\greannotation{Ant.}
\greannotation{8g}
\psalm{dixit-jesus}{Magnificat}{8g}{1-0-1-2}

\clearpage
\subsection{Intercessions}
\gresetinitiallines{0}
 \iflect
 \gabcsnippet{
     (c4)With(f) joy(gh) in(h) our(h) hearts,(h) let(h) us(h) call(h) u(h)pon(h)
     Christ(h) the(h) Lord,(h)
     who(h) died(h) and(h) rose(g) a(ixi)gain,(h)
     — and(h) lives(h) al(h)ways(h) to(h) in(h)ter(h)cede(g) for(f) pray:(g.)
 }
 \fi
\ifchoir %\emph{Recto tono.}
 \gabcsnippet{
     (c4) Vic(g)to(g)rious(g) King,(g) hear(g) our(h) prayer.(f.)
 }
\fi
\begin{multicols}{2}
    \small
\iflect\else
With joy in our hearts, let us call upon Christ the Lord,
who died and rose again,\\
— and lives always to intercede for us:\\
\textbf{Victorious King, hear our prayer.}\fi

With joy in our hearts, let us call upon Christ the Lord, who died and rose again,\\
— and lives always to intercede for us:\\
\textbf{Victorious King, hear our prayer.}

Light and salvation of all peoples, send into our hearts the fire of your Spirit,\\
— as we proclaim your resurrection.\\
\textbf{Victorious King, hear our prayer.}

Let Israel recognize in you her longed-for Messiah,\\
— and the whole earth be filled with the knowledge of your glory.\\
\textbf{Victorious King, hear our prayer.}

Keep us in the communion of your saints,\\
— and grant us rest from our labors in their company.\\
\textbf{Victorious King, hear our prayer.}

You have triumphed over death, your enemy; destroy in us the power of death,\\
— that we may live only for you, victorious and immortal Lord.\\
\textbf{Victorious King, hear our prayer.}

Savior Christ, you were obedient even to accepting death, and were raised up to the right hand of the Father,\\
— in your goodness welcome your brothers and sisters into the kingdom of your glory.\\
\textbf{Victorious King, hear our prayer.}
\end{multicols}

\subsubsection{Our Father}
\gresetinitiallines{0}
\gregorioscore{Communes/pater-noster/English-C}
\gresetinitiallines{1}

\subsubsection{Prayer \& Dismissal}
\iflect
\gabcsnippet{
    (c3) May(h) your(h) peo(h)ple(h) ex(h)ult(h) for(h) ev(h)er,(h) O(h) God,(h) in(h) re(h)newed(h) youth(h)ful(h)ness(h) of(h) <b>spir</b>(h)it,(f) †(,) so(h) that,(h) re(h)joic(h)ing(h) now(h) in(h) the(h) re(h)stored(h) glo(h)ry(h) of(h) <i>our</i>(g) <i>a</i>(f)<b>dop</b>(h)tion,(h.) (;) we(h) may(h) look(h) for(h)ward(h) in(h) con(h)fi(h)dent(h) hope(h)
    to(h) the(h) re(h)joic(h)ing(h) of(h) the(h) day(h) of(h) res(h)ur(h)<b>rec</b>(h)tion.(d.) (:) Through(h) our(h) Lord(h) Je(h)sus(h) <i>Christ</i>,(g) <i>your</i>(f) <b>Son</b>,(h.) (;) who(h) lives(h) and(h) reigns(h) with(h) you(h) in(h) the(h) u(h)ni(h)ty(h) of(h) the(h) <i>Ho</i>(g)<i>ly</i>(f) <b>Spir</b>(h)it,(h.) (;) God,(h) for(h) ev(h)er(h) and(h) <b>ev</b>(h)er.(f.) (::) —A(h)men.(h.) (::)
    }
\else
{\small
May your people exult for ever, O God,
in renewed youthfulness of spirit,
so that, rejoicing now in the restored glory of our adoption,
we may look forward in confident hope
to the rejoicing of the day of resurrection.
Through our Lord Jesus Christ, your Son,
who lives and reigns with you in the unity of the Holy Spirit,
God, for ever and ever.
— \textbf{Amen}.}\fi

%%\begin{multicols}{2}
%%    \small
%%\emph{If a priest or deacon presides:}\\
%%The Lord be with you.\\
%%— \textbf{And with your spirit.}\\
%%May almighty God bless you,\\
%%the Father, and the Son, and the Holy Spirit.\\
%%— \textbf{Amen}.\\
%%Go in peace.\\
%%— \textbf{Thanks be to God.}
%%
%%\columnbreak
%%
%%\emph{In the absence of a priest or deacon and in individual recitation, Evening Prayer concludes:}
\iflect
%\input{C:/Users/johna/Chant/Communes/dominus-nos-benedicat/english-solemn.gtex}
\gabcsnippet{(c3) May(h) the(g) LORD(f) bless(h) us,(h.) (;) pro(h)tect(h) us(h) from(g) all(f) e(h)vil,(h.) (;) and(h) bring(h) us(h) to(h) ev(h)er(h)last(h)ing(h) life.(f.) (::)}
\fi

\begin{center}
    \iflect
    %\gabcsnippet{
    %    (c3) May(h) the(h) lord(g) bless(f) us,(h.) (;) pro(h)tect(h) us(h) from(g) all(f) e(h)vil,(h.) (;) and(h) bring(h) us(h) to(h) ev(h)er(h)last(h)ing(f) life.(f.) (:) —A(g.)men.(h.) (::)
    %}
    \else
    May the Lord + bless us, %\\
protect us from all evil %\\
and bring us to everlasting life.
— \textbf{Amen}.\\
\fi

\emph{The Antiphon Regina Cæli
    %to the Blessed Virgin Mary 
    is traditionlly sung at Night Prayer
    (Compline) throughout the Easter Season.}
\end{center}

\gregorioscore{hymns/regina-caeli/solesmes.gabc}

\end{document}