% !TEX root = root.tex
% !TEX recipe = LuaLaTeX+se
%\documentclass{article}
\documentclass[parskip]{scrartcl} % set document class: manual at https://ctan.org/pkg/koma-script
%\usepackage{fontspec}

% Load packages:
\usepackage[osf,p]{libertine} % set font
\usepackage[autocompile]{gregoriotex} % enable Gregorio score inclusion
\usepackage[latin]{babel} % set language
\usepackage{multicol}
\usepackage[margin=3cm]{geometry}
\usepackage{scrlayer-scrpage}

\newenvironment{verses}[1][2]{
\begin{multicols}{#1}
\footnotesize
}{
\end{multicols}}

\setkomafont{section}{\normalfont\centering\huge\scshape} % section heading style
\setkomafont{subsection}{\normalfont\centering\Large\scshape} % section heading style
\setkomafont{subsubsection}{\normalfont\centering\small\scshape} % section heading style
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\setkomafont{pagehead}{\scshape}
\automark[section]{section}
%\automark*[subsection]{subsection}

%\lohead[\thesection]
%{\thesection}
%\rohead[\thesubsection]
%{\thesubsection}
\pagestyle{scrheadings}

\def\translation{NABRE}

% Set the space around the initial:
% See http://gregorio-project.github.io/gregoriotex/details.html for more details and options
\grechangedim{beforeinitialshift}{2.2mm}{scalable}
\grechangedim{afterinitialshift}{2.2mm}{scalable}

% Set the initial font (change 43 for a larger size):
%\grechangestyle{initial}{\fontsize{43}{43}\selectfont}%

% Make staff lines red; remove for black:
%\gresetlinecolor{gregoriocolor}

% Use the "commentary" field of the score in the top right corner:
\gresetheadercapture{commentary}{grecommentary}{string}

% Format annotation above initial
\grechangestyle{annotation}{\small\bfseries}

\begin{document}

\thispagestyle{plain}
\section{Laudes -- Assumption of the Blessed Virgin Mary}
\begin{center}
    \greseparator{3}{20}
\end{center}

\subsection{Introduction}
\input{C:/Users/johna/Chant/Communes/deus-in-adjutorium/festivus.gtex}
\begin{center}
    \emph{Oh God, come to my assistance. --\textbf{LORD, make haste to help me.}\\
    Glory be to the Father, and to the Son, and to the Holy Spirit.
    --\textbf{As it was in the beginning, is now, and ever shall be, world with out end. Amen. Alleluia.}}
    % \greseparator{3}{20}
\end{center}

% Lucis creator (LHymn 188)
\input{C:/Users/johna/Chant/hymns/solis-o-virgo/eng.tex}

\subsection{Psalmody}
\input{C:/Users/johna/Chant/Antiphona/pulchra-est-decora/dbl.tex}
\input{C:/Users/johna/Chant/Antiphona/virgo-gloriosa-Maria/dbl.tex}
\input{C:/Users/johna/Chant/Antiphona/in-odore/dbl.tex}



\subsection{Reading \hfill See Isaiah 61:10}
I rejoice heartily in the Lord,\\
   in my God is the joy of my soul;\\
For he has clothed me with a robe of salvation,\\
   and wrapped me in a mantle of justice,\\
   like a bride bedecked with her jewels.

\input{C:/Users/johna/Chant/Resp-breve/hodie-maria/lat.tex}

\subsection{Gospel Canticle}
\input{C:/Users/johna/Chant/Antiphona/virgo-prudentissima/dbl.tex}

\subsection{Intercessions}

Let us glorify our Savior, who chose the Virgin Mary for his mother. Let us ask him:\\
May your mother intercede for us, Lord.

Eternal Word, you chose Mary as the uncorrupted ark of your dwelling place,\\
— free us from the corruption of sin.\\
May your mother intercede for us, Lord.

You are our redeemer, who made the immaculate Virgin Mary your purest home and the sanctuary of the Holy Spirit,\\
— make us temples of your Spirit for ever.\\
May your mother intercede for us, Lord.

King of kings, you lifted up your mother, body and soul into heaven,\\
— help us to fix our thoughts on things above.\\
May your mother intercede for us, Lord.

Lord of heaven and earth, you crowned Mary and set her at your right hand as queen,\\
— make us worthy to share this glory.\\
May your mother intercede for us, Lord.

\subsubsection{Our Father}
\input{C:/Users/johna/Chant/Communes/pater-noster/English-C.gtex}

%\gresetinitiallines{0} 
%\gresetinitiallines{1} 

\subsubsection{Prayer}

Almighty, ever-living God,\\
who assumed the Immaculate Virgin Mary, the Mother of your Son,\\
body and soul into heavenly glory,\\
grant, we pray,\\
that, always attentive to the things that are above,\\
we may merit to be sharers of her glory.\\
Through our Lord Jesus Christ, your Son,\\
who lives and reigns with you in the unity of the Holy Spirit,\\
God, for ever and ever.\\
— \textbf{Amen}.

\subsubsection{Dismissal}
\emph{If a priest or deacon presides, he dismisses the people:}

The Lord be with you.\\
— \textbf{And with your spirit.}

May almighty God bless you,\\
the Father, and the Son, and the Holy Spirit.\\
— \textbf{Amen}.

\emph{Another form of the blessing may be used, as at Mass.}

Then he adds:

Go in peace.\\
— \textbf{Thanks be to God.}

\emph{In the absence of a priest or deacon and in individual recitation, Evening Prayer concludes:}

May the Lord + bless us,\\
protect us from all evil\\
and bring us to everlasting life.
— \textbf{Amen}.

\end{document}