% !TEX root = OT-B31-II-Vespers.tex
% !TEX recipe = LuaLaTeX+se
%\documentclass{article}
\documentclass[parskip]{scrartcl} % set document class: manual at https://ctan.org/pkg/koma-script
%\usepackage{fontspec}

% Load packages:
\usepackage[osf,p]{libertine} % set font
\usepackage[autocompile]{gregoriotex} % enable Gregorio score inclusion
\usepackage[latin]{babel} % set language
\usepackage{multicol}
\usepackage[margin=2cm]{geometry}
\usepackage{scrlayer-scrpage}

\newenvironment{verses}[1][2]{
\begin{multicols}{#1}
\footnotesize
}{
\end{multicols}}

\setkomafont{section}{\normalfont\centering\huge\scshape} % section heading style
\setkomafont{subsection}{\normalfont\centering\Large\scshape} % section heading style
\setkomafont{subsubsection}{\normalfont\centering\small\scshape} % section heading style
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\setkomafont{pagehead}{\scshape}
%\automark[section]{section}
%\automark*[subsection]{subsection}

%\lohead[\thesection]
%{\thesection}
%\rohead[\thesubsection]
%{\thesubsection}
%\pagestyle{scrheadings}

\newif\ifchoir
\choirfalse

\newif\iflect
\lectfalse

\def\translation{NABRE}

% Set the space around the initial:
% See http://gregorio-project.github.io/gregoriotex/details.html for more details and options
\grechangedim{beforeinitialshift}{2.2mm}{scalable}
\grechangedim{afterinitialshift}{2.2mm}{scalable}

% Set the initial font (change 43 for a larger size):
%\grechangestyle{initial}{\fontsize{43}{43}\selectfont}%

% Make staff lines red; remove for black:
%\gresetlinecolor{gregoriocolor}

% Use the "commentary" field of the score in the top right corner:
\gresetheadercapture{commentary}{grecommentary}{string}

% Format annotation above initial
\grechangestyle{annotation}{\small\bfseries}

\begin{document}

\thispagestyle{plain}
\iflect
\section{Vespers II -- Sunday, Nov. 3, 2024 LECTIONARY}
\else
\ifchoir
\section{Vespers II -- Sunday, Nov. 3, 2024 CHOIR}
\else
\section{Vespers II -- Sunday, Nov. 3, 2024}
\begin{center}
    \vspace{-0.5cm}
%    \emph{31st Sunday in Ordinary Time, Year B}
    %\emph{Prepared by Dr. J. Costanzo}
    %
    %    \greseparator{3}{30}
\end{center}
\vspace{-1cm}
\fi
\fi

\subsection{Introduction}
\marginpar{\small\scshape Stand}
\iflect
\input{C:/Users/johna/Chant/Communes/deus-in-adjutorium/festivus.gtex}
\else
\ifchoir
\input{C:/Users/johna/Chant/Communes/deus-in-adjutorium/festivus.gtex}
\else
\begin{center}
    \vspace{-0.5cm}
    \emph{Oh God, come to my assistance. --\textbf{LORD, make haste to help me.}\\
    Glory be to the Father, and to the Son, and to the Holy Spirit.
    --\textbf{As it was in the beginning, is now, and ever shall be, world with out end. Amen. Alleluia.}}
    
    \vspace{-0.5cm}
    %\greseparator{3}{30}
\end{center}
\fi
\fi

% Lucis creator (LHymn 188)
\subsubsection*{Hymn: ``Lucis Creator'' \hfill
{\small\itshape Attr. St. Gregory the Great, ca 540-604; tr. © 2023 ICEL}}
\ifchoir
\input{C:/Users/johna/Chant/hymns/lucis-creator/in-aestate_ICEL_full.gtex}
\else
\input{C:/Users/johna/Chant/hymns/lucis-creator/in-aestate_v1-ICEL.gtex}
    \begin{multicols}{2}
    \input{C:/Users/johna/Chant/hymns/lucis-creator/verses-ICEL.tex}
    \vspace{-0.5cm}
\end{multicols}
\fi

\subsection{Psalmody}
\marginpar{\small\scshape Sit}
\vspace*{-5pt}
%% FIRST PSALM %%
\input{C:/Users/johna/Chant/Antiphona/dixit-dominus/dbl.tex}

\vspace*{-15pt}
\subsubsection{2nd Antiphon}
\vspace*{-15pt}

%% SECOND PSALM %%
\input{C:/Users/johna/Chant/Antiphona/fidelia-omnia/dbl.tex}


%% NT CANTICLE %%
\subsubsection*{Canticle: See Rev. 19:1-7}
\ifchoir
\input{C:/Users/johna/Chant/Canticum/salus-et-gloria/english-VI.gtex}
\else
\begin{multicols}{2}
    \small
    \input{C:/Users/johna/Chant/Canticum/salus-et-gloria/text.tex}    
\end{multicols}
\begin{center}
    \greseparator{3}{30}
\end{center}
\fi


\subsection{Reading}
\vspace{-0.5cm}
{\tiny \hfill 1 Peter 1:3-5}\\
\iflect
\gresetinitiallines{0}
\gregorioscore{IIVesp-lect.gabc}
\gresetinitiallines{1}
\else
Praised be the God and Father
of our Lord Jesus Christ,\\
he who in his great mercy
gave us new birth;\\
a birth unto hope which draws its life
from the resurrection of Jesus Christ from the dead;\\
a birth to an imperishable inheritance,
incapable of fading or defilement,\\
which is kept in heaven for you
who are guarded with God’s power through faith;\\
a birth to a salvation which stands ready
to be revealed in the last days.
\fi
\vspace{-0.5cm}

\subsubsection{Responsory}
\ifchoir
\input{C:/Users/johna/Chant/Resp-breve/benedictus-es-domine/english-extended.gtex}
\else
\input{C:/Users/johna/Chant/Resp-breve/benedictus-es-domine/english.gtex}
\fi

\subsection{Gospel Canticle}
\marginpar{\small\scshape Stand}
%\vspace{-0.5cm}
\input{C:/Users/johna/Chant/Antiphona/diligamus-nos/dbl.tex}

%\iflect\else\ifchoir\else\clearpage\fi\fi
\subsection{Intercessions}
\vspace{-0.5cm}
\iflect\gregorioscore{IIV-inter.gabc}\else
\ifchoir\gregorioscore{IIV-inter-resp.gabc}\fi\fi
\begin{multicols}{2}
    \small
\iflect\else The world was created by the Word of God, re-created by his redemption, and it is continually renewed by his love.\\
— Rejoicing in him we call out:\\
\textbf{Renew the wonders of your love, Lord.}\fi

We give thanks to God whose power is revealed in nature, *\\
— and whose providence is revealed in history.\\
\textbf{Renew the wonders of your love, Lord.}

Through your Son, the herald of reconciliation, the victor of the cross, *\\
— free us from empty fear and hopelessness.\\
\textbf{Renew the wonders of your love, Lord.}

May all those who love and pursue justice, *\\
— work together without deceit to build a world of true peace.\\
\textbf{Renew the wonders of your love, Lord.}

Be with the oppressed, free the captives, console the sorrowing, feed the hungry, strengthen the weak, *\\
— in all people reveal the victory of your cross.\\
\textbf{Renew the wonders of your love, Lord.}

After your Son’s death and burial you raised him up again in glory, *\\
— grant that the faithful departed may live with him.\\
\textbf{Renew the wonders of your love, Lord.}
\end{multicols}

\subsubsection{Our Father}
\vspace{-0.5cm}
\gresetinitiallines{0}
\input{C:/Users/johna/Chant/Communes/pater-noster/English-C.gtex}
\gresetinitiallines{1}

\subsubsection{Prayer}
\vspace{-0.5cm}
Almighty and merciful God,
by whose gift your faithful offer you
right and praiseworthy service,
grant, we pray,
that we may hasten without stumbling
to receive the things you have promised.
Through our Lord Jesus Christ, your Son,
who lives and reigns with you in the unity of the Holy Spirit,
God, for ever and ever.
— \textbf{Amen}.

\subsubsection{Dismissal}
%%\begin{multicols}{2}
%%    \small
%%\emph{If a priest or deacon presides:}\\
%%The Lord be with you.\\
%%— \textbf{And with your spirit.}\\
%%May almighty God bless you,\\
%%the Father, and the Son, and the Holy Spirit.\\
%%— \textbf{Amen}.\\
%%Go in peace.\\
%%— \textbf{Thanks be to God.}
%%
%%\columnbreak
%%
%%\emph{In the absence of a priest or deacon and in individual recitation, Evening Prayer concludes:}
\iflect\input{C:/Users/johna/Chant/Communes/dominus-nos-benedicat/english-solemn.gtex}
\else\vspace{-0.5cm}
May the Lord + bless us, %\\
protect us from all evil %\\
and bring us to everlasting life.
— \textbf{Amen}.\fi
%\end{multicols}


\end{document}