% !TEX root = 8-OT-C-VII.tex
% !TEX recipe = LuaLaTeX+se
%\documentclass{article}
\documentclass[paper=letter,parskip]{scrartcl} % set document class: manual at https://ctan.org/pkg/koma-script
%\usepackage{fontspec}

% Load packages:
\usepackage[osf,p]{libertine} % set font
\usepackage[autocompile]{gregoriotex} % enable Gregorio score inclusion
\usepackage[latin]{babel} % set language
\usepackage{multicol}
\usepackage[margin=2cm]{geometry}
\usepackage{scrlayer-scrpage}

\newcommand{\myhome}{C:/Users/johna/Chant/}
\gresetgregpath{{\myhome}}

\setkomafont{section}{\normalfont\centering\huge\scshape\bfseries} % section heading style
\setkomafont{subsection}{\normalfont\centering\Large\scshape} % section heading style
\setkomafont{subsubsection}{\normalfont\centering\small\scshape} % section heading style
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\setkomafont{pagehead}{\scshape}
%\automark[section]{section}
%\automark*[subsection]{subsection}

%spacing before and after headers
\RedeclareSectionCommand[
  %runin=false,
  afterindent=false,
  beforeskip=.25\baselineskip,
  afterskip=.15\baselineskip]{subsubsection}
\RedeclareSectionCommand[
%runin=false,
    afterindent=false,
    beforeskip=.25\baselineskip,
    afterskip=.15\baselineskip]{subsection}
\RedeclareSectionCommand[
    %runin=false,
    afterindent=false,
    beforeskip=.25\baselineskip,
    afterskip=.15\baselineskip]{section}
\RedeclareSectionCommand[
    runin=false,
    afterindent=false,
    beforeskip=3.25ex plus 1ex minus .2ex,
    afterskip=3pt]{paragraph}
%\lohead[\thesection]
%{\thesection}
%\rohead[\thesubsection]
%{\thesubsection}
%\pagestyle{scrheadings}

\usepackage{soul}
\sethlcolor{white}
\let\oldhl\hl
\renewcommand{\hl}[1]{\ifchoir \oldhl{#1} \else #1 \fi}


\newif\iflect
\lectfalse

\newif\ifchoir
\choirfalse

\iflect\choirtrue\fi


% Set the space around the initial:
% See http://gregorio-project.github.io/gregoriotex/details.html for more details and options
\grechangedim{beforeinitialshift}{2.2mm}{scalable}
\grechangedim{afterinitialshift}{2.2mm}{scalable}
 
% Set the initial font (change 43 for a larger size):
%\grechangestyle{initial}{\fontsize{43}{43}\selectfont}%

% Make staff lines red; remove for black:
%\gresetlinecolor{gregoriocolor}

% Use the "commentary" field of the score in the top right corner:
\gresetheadercapture{commentary}{grecommentary}{string}
\grechangedim{commentaryseparation}{0.15mm}{scalable}

% Format annotation above initial
\grechangestyle{annotation}{\small\bfseries}


\newcommand{\hymn}[3]{
\subsubsection*{Hymn: ``#2'' \hfill
{\small\itshape #3}}
\ifchoir
\gregorioscore{hymns/#1/english.gabc}
\else
\gregorioscore{hymns/#1/english_v1.gabc}
    \begin{multicols}{2}
        \small
        \input{\myhome/hymns/#1/verses.tex}
\end{multicols}
\fi}

\newcommand{\introd}[1]{
    \subsection{Introduction}
    \marginpar{\small\scshape Stand}
    \ifchoir
    \gregorioscore{Communes/deus-in-adjutorium/#1}
    \else
    \begin{center}
        \emph{Oh God, come to my assistance. --\textbf{LORD, make haste to help me.}\\
        Glory be to the Father, and to the Son, and to the Holy Spirit.
        --\textbf{As it was in the beginning, is now, and ever shall be, world with out end. Amen. Alleluia.}}
        %\greseparator{3}{30}
    \end{center}
    \fi
}

\newcommand{\psalm}[4]{
    \gregorioscore{Antiphona/#1/solesmes.gabc}
    \gresetinitiallines{0}
    \ifchoir
    \gregorioscore{Psalms/#2/#3.gabc}
    \begin{multicols}{2}
        \small
        \input{\myhome/Psalms/#2/#4.tex}

        \input{\myhome/Psalms/GloriaPatri/#4.tex}
    \end{multicols}
    \else
    \begin{multicols}{2}
        \small
        \input{\myhome/Psalms/#2/all.tex}
    \end{multicols}
    \fi
    \gregorioscore{Antiphona/#1/english.gabc}
    \gresetinitiallines{1}
}

\newcommand{\responsory}[1]{
    \subsubsection{Responsory}
    \ifchoir
\gregorioscore{Resp-breve/#1/english-extended.gtex}
\else
\gregorioscore{Resp-breve/#1/english.gtex}
\fi
}

\begin{document}

\thispagestyle{plain}
\section{Sunday, Mar. 2, 2025 at Second Vespers \iflect LECTIONARY \else\ifchoir CHOIR\fi\fi}
\iflect
\else
\ifchoir
\else
%\begin{center}
%    \emph{Feast of the Presentation of the Lord}
    %\emph{Prepared by Dr. J. Costanzo}
    %
    %    \greseparator{3}{30}
%\end{center}
%\vspace{-0.5cm}
\fi
\fi

\introd{festivus}

\hymn{o-lux-beata-trinitas-hieme}{O lux, beata Trinitas}{7-8th c., tr. © 2023 ICEL.}

\vspace{-15pt}
\subsection{Psalmody}
\marginpar{\small\scshape Sit}
%% FIRST PSALM %%
\paragraph{Psalm 110[109]}
\greannotation{Ant. 1}
\greannotation{8G}
%\grecommentary{Ps. 110}
\psalm{ex-utero}{110}{8G}{1-0-1-2}

\clearpage
%% SECOND PSALM %%
\paragraph{Psalm 112[111]}
\greannotation{Ant. 2}
\greannotation{4a}
%\grecommentary{Ps. 130}
\psalm{in-mandatis}{112}{4a}{1-2-1-3}


%% NT CANTICLE %%
%\greannotation{Ant. 3}
%\greannotation{3a}
%\grecommentary{Col. 1:12-20}
%\psalm{viderunt-oculi-mei}{Col1-12}{3a}{2-0-2-0}
\paragraph{Canticle: Wedding Feast of the Lamb}
\emph{In Ordinary Time, the Antiphonale Romanum
provides no antiphon for this Canticle when the Office is sung.}
\ifchoir
\greannotation{Cant.}
\greannotation{6}
\gregorioscore{Canticum/salus-et-gloria/english-VI}
\else
\begin{multicols}{2}
    \input{Canticum/salus-et-gloria/text.tex}    
\end{multicols}
\fi

\clearpage
\subsection{Reading: Hebrews 12:22-24}
\iflect
\gresetinitiallines{0}
\gabcsnippet{
    (c3) You(h) have(h) drawn(h) near(h) to(h) Mount(h) Zi(h)on(h) and(h) the(h) cit(h)y(h) of(h) the(h) liv(g)ing(f) God,(h.) (;) the(h) heav(h)en(h)ly(h) Je(h)ru(h)sa(h)lem,(f) †(,) to(h) myr(h)i(h)ads(h) of(h) an(h)gels(h) in(h) fes(g)tal(f) gath(h)er(h)ing,(h.) (;)
    to(h) the(h) as(h)sem(h)bly(h) of(h) the(h) first-(h)born(h) en(h)rolled(g) in(f) heav(h)en,(h.) (;)
    to(h) God(h) the(h) judge(g) of(f) all,(h.) (;)
    to(h) the(h) spir(h)its(h) of(h) just(h) men(g) made(f) per(h)fect,(h.) (;)
    to(h) Je(h)sus,(h) the(h) me(h)di(h)a(h)tor(h) of(h) a(g) new(f) cov(h)e(h)nant,(h.) (;)
    and(h) to(h) the(h) sprin(h)kled(h) blood(h) which(h) speaks(h) more(h) el(h)o(h)quent(h)ly(h) than(h) that(h) of(f) A(e)bel.(ef..) (::)
}
\gresetinitiallines{1}
\else
You have drawn near to Mount Zion and the city of the living God,
the heavenly Jerusalem, to myriads of angels in festal gathering,
to the assembly of the first-born enrolled in heaven,
to God the judge of all,
to the spirits of just men made perfect,
to Jesus, the mediator of a new covenant,
and to the sprinkled blood which speaks more eloquently than that of Abel.
\fi

\greannotation{Resp.}
\greannotation{6}
\responsory{magnus-dominus-noster}


\subsection{Gospel Canticle}
\marginpar{\small\scshape Stand}
\grechangedim{commentaryraise}{3.5mm}{scalable}
\greannotation{Ant.}
\greannotation{8g}
\psalm{non-potest-arbor-bona-8g}{Magnificat}{8g}{1-0-1-2}

\clearpage
\subsection{Intercessions}
\gresetinitiallines{0}
\iflect\gabcsnippet{
    (c4)Re(f)joi(gh)cing(h) in(h) the(h) Lord,(h) from(h) whom(h) all(h)
    good(g) things(ixi) come,(h)
    — let(g) us(f) pray:(g.)
}\fi
\ifchoir\gabcsnippet{
    (c4)Lord,(g) hear(g) our(h) prayer.(f.)
}\fi
\begin{multicols}{2}
    \small
\iflect\else Rejoicing in the Lord, from whom all
good things come,\\
— let us pray:\\
\textbf{Lord, hear our prayer.}\fi

Father and Lord of all, you sent your Son into the world, that your name might be glorified in every place,\\
— strengthen the witness of your Church among the nations.\\
\textbf{Lord, hear our prayer.}

Make us obedient to the teachings of your apostles,\\
— and bound to the truth of our faith.\\
\textbf{Lord, hear our prayer.}

As you love the innocent,\\
— render justice to those who are wronged.\\
\textbf{Lord, hear our prayer.}

Free those in bondage and give sight to the blind,\\
— raise up the fallen and protect the stranger.\\
\textbf{Lord, hear our prayer.}

Fulfill your promise to those who already sleep in your peace,\\
— through your Son grant them a blessed resurrection.\\
\textbf{Lord, hear our prayer.}
\end{multicols}

\subsubsection{Our Father}
\gresetinitiallines{0}
\gregorioscore{Communes/pater-noster/English-C}
\gresetinitiallines{1}

\subsubsection{Prayer \& Dismissal}
\iflect
\gabcsnippet{
    (c4) Grant(g) us,(h) O(h) Lord,(h) we(h) pray,(g.) (;) that(g) the(h) course(h) of(h) the(h) world(h)
    may(h) be(h) di(h)rect(h)ed(h) by(h) your(h) peace(h)ful(h) rule(h)
    and(h) that(h) your(h) Church(h) may(h) re(h)joice,(g.) (;) un(g)trou(h)bled(h) in(h) her(g) de(g)vo(h)tion.(h.) (:) 
    Through(g) our(h) Lord(h) Je(h)sus(h) Christ,(g) your(g) Son,(h.) (;) who(g) lives(h) and(h) reigns(h) with(h) you(h) in(h) the(h) u(h)ni(h)ty(h) of(h) the(h) Ho(g)ly(g) Spir(h)it,(h.) (;) God,(h) for(h) ev(h)er(g) and(h) ev(hg)er.(g.) (:) —A(g)men.(gh..) (::)
    }
\else
Grant us, O Lord, we pray,
that the course of the world
may be directed by your peaceful rule
and that your Church may rejoice,
untroubled in her devotion.
Through our Lord Jesus Christ, your Son,
who lives and reigns with you in the unity of the Holy Spirit,
God, for ever and ever.
— \textbf{Amen}.\fi

%%\begin{multicols}{2}
%%    \small
%%\emph{If a priest or deacon presides:}\\
%%The Lord be with you.\\
%%— \textbf{And with your spirit.}\\
%%May almighty God bless you,\\
%%the Father, and the Son, and the Holy Spirit.\\
%%— \textbf{Amen}.\\
%%Go in peace.\\
%%— \textbf{Thanks be to God.}
%%
%%\columnbreak
%%
%%\emph{In the absence of a priest or deacon and in individual recitation, Evening Prayer concludes:}
\iflect\input{C:/Users/johna/Chant/Communes/dominus-nos-benedicat/english-solemn.gtex}\fi

\begin{center}
    \iflect
    %\gabcsnippet{
    %    (c3) May(h) the(h) lord(g) bless(f) us,(h.) (;) pro(h)tect(h) us(h) from(g) all(f) e(h)vil,(h.) (;) and(h) bring(h) us(h) to(h) ev(h)er(h)last(h)ing(f) life.(f.) (:) —A(g.)men.(h.) (::)
    %}
    \else
    May the Lord + bless us, %\\
protect us from all evil %\\
and bring us to everlasting life.
— \textbf{Amen}.\\
\fi

\emph{The Antiphon Ave Regina Cælorum
    to the Blessed Virgin Mary is traditionlly sung at Night Prayer
    (Compline) from February 2nd
    until the beginning of the Easter Season.}
\end{center}

\gregorioscore{hymns/ave-regina-caelorum/solesmes.gabc}

\end{document}