% In you, O Lord, I take refuge; *\\
% let me never be put to shame. \\
In your uprightness, rescue me, \textbf{free} me; *\\
incline your ear to \emph{me} and \textbf{save} me. 

Be my rock, my constant re\emph{fuge}, †\\
a mighty stronghold to \textbf{save} me, *\\
for you are my \emph{rock}, my \textbf{strong}hold. \\
My God, free me from the hand of the \textbf{wic}ked, *\\
from the grip of the unjust, of \emph{the} op\textbf{pres}sor. 

It is you, O Lord, who are \textbf{my} hope, *\\
my trust, O \emph{Lord}, from \textbf{my} youth. \\
On you I have leaned from my \emph{birth}; †\\
from my mother's womb, you have drawn \textbf{me} forth. *\\
At all \emph{times} I \textbf{give} you praise. 

My fate has filled many \textbf{with} awe, *\\
but you are my \emph{migh}ty \textbf{ref}uge. \\
My mouth is filled with \textbf{your} praise, *\\
with your glory, \emph{all} the \textbf{day} long. \\
Do not reject me now that I \textbf{am} old; *\\
when my strength fails do \emph{not} for\textbf{sake} me. 

For my enemies are speaking a\textbf{bout} me; *\\
those who watch me take coun\emph{sel} to\textbf{geth}er, \\
saying: ``God has forsaken him; \textbf{fol}low him. *\\ 
Seize him; there is no \emph{one} to \textbf{save} him.'' \\
O God, do not stay a\textbf{far} off; *\\
O my God, make \emph{haste} to \textbf{help} me! 

Let them be put to shame and \textbf{con}sumed, *\\
\emph{those} who \textbf{seek} my life. \\
Let them be covered with shame and con\textbf{fu}sion, *\\
those who \emph{seek} to \textbf{harm} me. 

But as for me, I will al\textbf{ways} hope, *\\
and \emph{praise} you \textbf{more} and more. \\
My mouth will tell of your just\emph{ice}, †\\
and all the day long of your sal\textbf{va}tion, *\\
though I can \emph{ne}ver \textbf{tell} it all. 

I will come with praise of your might, O \emph{Lord}; †\\
I will call to mind your \textbf{jus}tice, *\\
\emph{yours}, O \textbf{Lord}, alone. \\
O God, you have taught me from \textbf{my} youth, *\\
and I pro\emph{claim} your \textbf{won}ders still. 

Even till I am old and gray-\textbf{head}ed, *\\
do not for\emph{sake} me, \textbf{O} God. \\
Let me tell of your migh\textbf{ty} arm *\\
to every coming \emph{gen}e\textbf{ra}tion; 

Your strength and your justice, \textbf{O} God, *\\
reach to the \emph{high}est \textbf{hea}vens. \\
It is you who have worked such \textbf{won}ders. *\\
O God, \emph{who} is \textbf{like} you? 

You have made me witness many troubles and \textbf{e}vils, *\\
but you will \emph{give} me \textbf{back} my life. \\
You will raise me from the depths of \textbf{the} earth; *\\
you will exalt me and con\emph{sole} me \textbf{a}gain. 

So I will give you thanks on \textbf{the} lyre *\\
for your faithful\emph{ness}, O \textbf{my} God. \\
To you will I sing with \textbf{the} harp, *\\
to you, the Holy \emph{One} of \textbf{Is}rael. \\
When I sing to you, my lips shall shout \textbf{for} joy, *\\
and my soul, which \emph{you} have \textbf{re}deemed. 

And all the day long \textbf{my} tongue *\\
shall tell the tale \emph{of} your \textbf{jus}tice, \\
for they are put to shame and \textbf{dis}graced, *\\
those who \emph{sought} to \textbf{harm} me. 
