\item \textit{How} \textit{good} is God to \textbf{Is}-rael, \mediant
 to those \textit{who} are \textbf{pure} of heart! 

\item As for me, my feet came close to \textbf{stum}-bling; \mediant
 my steps \textit{had} al-\textbf{most} slipped, 

\item for I was filled with envy \textbf{of} the proud, \mediant
 when I saw how the \textit{wic}-ked \textbf{pros}-per. 

\item For them there are \textbf{no} pains; \mediant
 their bo-\textit{dies} are \textbf{sound} and sleek. 

\item They do not share in people’s \textbf{bur}-dens; \mediant
 they are not stric-\textit{ken} like \textbf{o}-thers. 

\item So they wear their pride like a \textbf{neck}-lace; \mediant
 they clothe them-\textit{selves} with \textbf{vio}-lence. 

\item With folds of fat, their \textbf{eyes} protrude. \mediant
 With imagination \textit{their} hearts \textbf{o}-verflow. 

\item They scoff; they speak with \textbf{mal}-ice. \mediant
 From on high they threa-\textit{ten} op-\textbf{pres}-sion. 

\item They have set their mouths in the \textbf{hea}-vens, \mediant
 and their tongues are \textit{roa}-ming \textbf{the} earth. 

\item So the people \textbf{turn} to them \mediant
 and drink \textit{in} all \textbf{their} words. 

\item Thus they say, “How can \textbf{God} know? \mediant
 Does the Most High have \textit{a}-ny \textbf{know}-ledge?” 

\item Look at them, such are the \textbf{wic}-ked; \mediant
 ever prospe-\textit{rous,} they \textbf{grow} in wealth. 

\item How useless to keep my \textbf{heart} pure, \mediant
 and wash my \textit{hands} in \textbf{in}-nocence, 

\item when I was stricken all \textbf{day} long, \mediant
 suffered punishment with \textit{each} new \textbf{mor}-ning. 

\item Then I said, “If I should \textbf{speak} like that, \mediant
 I should betray your children’s \textit{ge}-ne-\textbf{ra}-tion.” 

\item I strove to fathom this \textbf{pro}-blem, \mediant
 too hard for my \textit{mind} to \textbf{un}-derstand, 

\item until I entered the holy \textbf{place} of God, \mediant
 and came to \textit{dis}-cern \textbf{their} end. 

\item How slippery the paths on which you \textbf{set} them; \mediant
 you make them fall \textit{to} de-\textbf{struc}-tion. 

\item How suddenly they come to \textbf{their} ruin, \mediant
 swept away, de-\textit{stroyed} by \textbf{ter}-rors. 

\item Like a dream one wakes \textbf{from,} O Lord, \mediant
 when you wake you dismiss \textit{them} as \textbf{phan}-toms. 

\item And so when my heart grew em-\textbf{bit}-tered, \mediant
 and I was pierced to the depths \textit{of} my \textbf{be}-ing, 

\item I was stupid and did not \textbf{un}-derstand; \mediant
 I was like a \textit{beast} in \textbf{your} sight. 

\item As for me, I was always in your \textbf{pre}-sence; \mediant
 you were holding me \textit{by} my \textbf{right} hand. 

\item By your counsel you will \textbf{guide} me, \mediant
 and then you will lead \textit{me} to \textbf{glo}-ry. 

\item What else have I in heaven \textbf{but} you? \mediant
 Apart from you, I want \textit{no}-thing \textbf{on} earth. 

\item My flesh and my heart waste \textit{a}-\textit{way;} \flex
God is the strength of \textbf{my} heart, \mediant
 my por-\textit{tion} for-\textbf{ev}-er. 

\item Surely, those who are far from you \textbf{pe}-rish; \mediant
 you put an end to all those who \textit{are} un-\textbf{faith}-ful. 

\item For me to be near God \textbf{is} good; \mediant
 I have made the Lord \textit{GOD} my \textbf{re}-fuge. 

\item I will proclaim \textbf{your} works \mediant
 at the gates of \textit{daugh}-ter \textbf{Zi}-on. 
