%Save me, O God, for the waters *\\
%have risen to my neck. \\
I have sunk into the mud of \textbf{the} deep, *\\
where there \emph{is} no \textbf{foot}hold. \\
I have entered the waters of \textbf{the} deep, *\\
where the flood \emph{o}ver\textbf{whelms} me.

I am wearied with crying \textbf{a}loud; *\\
\emph{my} throat \textbf{is} parched. \\
My eyes are wasted \textbf{a}way \\
with \emph{wait}ing \textbf{for} my God. 

More numerous than the hairs on \textbf{my} head *\\
are those who hate \emph{me} with\textbf{out} cause. \\
Mighty are those who at\textbf{tack} me, *\\
e\emph{ne}mies \textbf{with} lies. \\
What I have never \textbf{sto}len, *\\
how \emph{can} I \textbf{re}store? 

O God, you know my \textbf{fo}lly; *\\
from you my sins \emph{are} not \textbf{hid}den. \\
May those who hope in you not \textbf{be} shamed *\\
because of \emph{me}, O \textbf{Lord} of hosts; \\
may those who seek you not be put \textbf{to} shame *\\
because of me, O \emph{God} of \textbf{Is}-ra-el.

It is for you that I suf\textbf{fer} taunts, *\\
that shame has \emph{cov}ered \textbf{my} face. \\
To my own kin I have become an \textbf{out}cast, *\\
a stranger to the children \emph{of} my \textbf{moth}er. \\
Zeal for your house con\textbf{sumes} me, *\\
and taunts a\emph{gainst} you \textbf{fall} on me.

When my soul wept bitterly in \textbf{fast}ing, *\\
they made it a \emph{taunt} a\textbf{gainst} me. \\
When I made my clothing \textbf{sack}cloth, *\\
I became \emph{a} re\textbf{proach} to them, \\
the gossip of those at \textbf{the} gates, *\\
the \emph{theme} of \textbf{drunk}ards' songs. 

But I pray to you, \textbf{O} Lord, *\\
at an ac\emph{cept}a\textbf{ble} time. \\
2In your great mercy, answer me, \textbf{O} God, *\\
with your faith\emph{ful} sal\textbf{va}tion. \\
Rescue me from \textbf{the} mire, *\\
lest \emph{I} be\textbf{gin} to sink. 

From those who hate me, deliver \emph{me}, +\\
and from the waters of \textbf{the} deep, *\\
lest the waves \emph{o}ver\textbf{whelm} me. \\
Let not the deep en\textbf{gulf} me, *\\
nor the pit \emph{close} its \textbf{mouth} on me.

Lord, answer, for your mercy \textbf{is} kind; *\\
in your great compas\emph{sion}, turn \textbf{t'wards} me. \\
Do not hide your face from your \textbf{ser}vant; *\\
answer me quickly, for I \emph{am} in \textbf{dis}tress. \\
Come close to my soul and re\textbf{deem} me; *\\
ransom me be\emph{cause} of \textbf{my} foes.

You know my taunts, my shame, my dis\textbf{hon}or; *\\
my oppressors are \emph{all} be\textbf{fore} you. \\
Taunts have broken \textbf{my} heart; *\\
here I \emph{am} in \textbf{an}guish. \\
I looked for solace, but there \textbf{was} none; *\\
for consolers, not \emph{one} could \textbf{I} find.

For food they gave \textbf{me} gall; *\\
in my thirst they gave me \emph{vi}ne\textbf{gar} to drink. \\
Let their table be a snare \textbf{to} them, *\\
and \emph{for} their \textbf{friends}, a trap. \\
Let their eyes grow \textbf{dim} and blind; *\\
let their limbs continu\emph{al}ly \textbf{trem}ble.

Pour out your anger u\textbf{pon} them; *\\
let your burning fury \emph{o}ver\textbf{take} them. \\
Let their camp be left \textbf{de}solate; *\\
let no one \emph{dwell} in \textbf{their} tents: \\
for they persecute one whom \textbf{you} struck; *\\
they increase the pain of one \emph{whom} you \textbf{wound}ed.

Charge them with guilt u\textbf{pon} guilt; *\\
let them have no share \emph{in} your \textbf{jus}tice. \\
Blot them out from the book of the \textbf{liv}ing; *\\
do not enroll them a\emph{mong} the \textbf{up}right. \\
As for me in my poverty \textbf{and} pain, *\\
let your salvation, O \emph{God}, raise \textbf{me} up. 

Then I will praise God's name with \textbf{a} song; *\\
I will glorify him \emph{with} thanks\textbf{giv}ing: \\
a gift pleasing the Lord more than \textbf{ox}en, *\\
more than a \emph{bull} with \textbf{horns} and hooves. 

The poor when they see it will \textbf{be} glad, *\\
and God-seeking \emph{hearts} will \textbf{re}vive; \\
for the Lord attends to the \textbf{need}y, *\\
and does not spurn his \emph{own} in \textbf{their} chains. \\
Let the heavens and the earth give \textbf{him} praise, *\\
the seas and every\emph{thing} that \textbf{moves} in them. 

For God will bring salvation to Zi-\emph{on}, +\\ 
and rebuild the cities of \textbf{Ju}dah, *\\
and they shall dwell there \emph{in} pos\textbf{ses}sion. \\
The children of his servants shall in\textbf{her}it it; *\\
those who love his \emph{name} shall \textbf{dwell} there. 
