Save me, O God, for the waters *\\
have risen to my neck. \\
I have sunk into the mud of the deep, *\\
where there is no foothold. \\
I have entered the waters of the deep, *\\
where the flood overwhelms me.

I am wearied with crying aloud; *\\
my throat is parched. \\
My eyes are wasted away \\
with waiting for my God. 

More numerous than the hairs on my head *\\
are those who hate me without cause. \\
Mighty are those who attack me, *\\
enemies with lies. \\
What I have never stolen, *\\
how can I restore? 

O God, you know my folly; *\\
from you my sins are not hidden. \\
May those who hope in you not be shamed *\\
because of me, O Lord of hosts; \\
may those who seek you not be put to shame *\\
because of me, O God of Israel.

It is for you that I suffer taunts, *\\
that shame has covered my face. \\
To my own kin I have become an outcast, *\\
a stranger to the children of my mother. \\
Zeal for your house consumes me, *\\
and taunts against you fall on me.

When my soul wept bitterly in fasting, *\\
they made it a taunt against me. \\
When I made my clothing sackcloth, *\\
I became a reproach to them, \\
the gossip of those at the gates, *\\
the theme of drunkards' songs. 

But I pray to you, O Lord, *\\
at an acceptable time. \\
In your great mercy, answer me, O God, *\\
with your faithful salvation. \\
Rescue me from the mire, *\\
lest I begin to sink. 

From those who hate me, deliver me, +\\
and from the waters of the deep, **\\
lest the waves overwhelm me. \\
Let not the deep engulf me, *\\
nor the pit close its mouth on me.

Lord, answer, for your mercy is kind; *\\
in your great compassion, turn towards me. \\
Do not hide your face from your servant; *\\
answer me quickly, for I am in distress. \\
Come close to my soul and redeem me; *\\
ransom me because of my foes.

You know my taunts, my shame, my dishonor; *\\
my oppressors are all before you. \\
Taunts have broken my heart; *\\
here I am in anguish. \\
I looked for solace, but there was none; *\\
for consolers—not one could I find.

For food they gave me gall; *\\
in my thirst they gave me vinegar to drink. \\
Let their table be a snare to them, *\\
and for their friends, a trap. \\
Let their eyes grow dim and blind; *\\
let their limbs continually tremble.

Pour out your anger upon them; *\\
let your burning fury overtake them. \\
Let their camp be left desolate; *\\
let no one dwell in their tents: \\
for they persecute one whom you struck; *\\
they increase the pain of one whom you wounded.

Charge them with guilt upon guilt; *\\
let them have no share in your justice. \\
Blot them out from the book of the living; *\\
do not enroll them among the upright. \\
As for me in my poverty and pain, *\\
let your salvation, O God, raise me up. 

Then I will praise God's name with a song; *\\
I will glorify him with thanksgiving: \\
a gift pleasing the Lord more than oxen, *\\
more than a bull with horns and hooves. 

The poor when they see it will be glad, *\\
and God-seeking hearts will revive; \\
for the Lord attends to the needy, *\\
and does not spurn his own in their chains. \\
Let the heavens and the earth give him praise, *\\
the seas and everything that moves in them. 

For God will bring salvation to Zion, +\\ 
and rebuild the cities of Judah, *\\
and they shall dwell there in possession. \\
The children of his servants shall inherit it; *\\
those who love his name shall dwell there. 
