% Not to us, Lord, not to us, *\\
% but to your name give the glory\\
for the sake of your love and \textbf{your} truth, *\\
lest the heathen say: ``\emph{Where} is \textbf{their} God?''

But our God is in the \textbf{heav}ens; *\\
he does what\emph{ev}er \textbf{he} wills.\\
Their idols are silver \textbf{and} gold, *\\
the \emph{work} of \textbf{hu}man hands.

They have mouths but they can\textbf{not} speak; *\\
they have eyes but \emph{they} can\textbf{not} see;\\
they have ears but they can\textbf{not} hear; *\\
they have nostrils but \emph{they} can\textbf{not} smell.

With their hands they cannot feel; †\\
with their feet they can\textbf{not} walk. *\\
No sound \emph{comes} from \textbf{their} throats.\\
Their makers will come to be \textbf{like} them *\\
and so will \emph{all} who \textbf{trust} in them.

Sons of Israel, trust in \textbf{the} Lord; *\\
he is their \emph{help} and \textbf{their} shield.\\
Sons of Aaron, trust in \textbf{the} Lord; *\\
he is their \emph{help} and \textbf{their} shield.

You who fear him, trust in \textbf{the} Lord; *\\
he is their \emph{help} and \textbf{their} shield.\\
He remembers us, and he will bless us; †\\
he will bless the sons of \textbf{Is}rael. *\\
He will bless the \emph{sons} of \textbf{Aa}ron.

The Lord will bless those who \textbf{fear} him, *\\
the little no \emph{less} than \textbf{the} great:\\
to you may the Lord grant \textbf{in}crease, *\\
to you and \emph{all} your \textbf{child}ren.

May you be blessed by \textbf{the} Lord, *\\
the maker of \emph{hea}ven \textbf{and} earth.\\
The heavens belong to \textbf{the} Lord *\\
but the earth he has \emph{gi}ven \textbf{to} men.

The dead shall not praise \textbf{the} Lord, *\\
nor those who go down in\emph{to} the \textbf{sil}ence.\\
But we who live bless \textbf{the} Lord *\\
now and for \emph{ev}er. \textbf{A}men.
