%Not to us, Lord, not to us, *\\
%but to your name give the glory\\
for the sake of your \textbf{love} and \textbf{your} truth, *\\
lest the heathen say: \textbf{“Where} is \textbf{their} God?”

But our God is \textbf{in} the \textbf{hea}-vens; *\\
he does what\textbf{ev}er \textbf{he} wills.\\
Their idols are \textbf{sil}ver \textbf{and} gold, *\\
the \textbf{work} of \textbf{hu}man hands.

They have mouths but \textbf{they} can\textbf{not} speak; *\\
they have eyes but \textbf{they} can\textbf{not} see;\\
they have ears but \textbf{they} can\textbf{not} hear; *\\
they have nostrils but \textbf{they} can\textbf{not} smell.

With their hands they cannot feel; †\\
with their feet \textbf{they} can\textbf{not} walk. *\\
No sound \textbf{comes} from \textbf{their} throats.\\
Their makers will \textbf{come} to be \textbf{like} them *\\
and so will \textbf{all} who \textbf{trust} in them.

Sons of Israel, \textbf{trust} in \textbf{the} Lord; *\\
he is their \textbf{help} and \textbf{their} shield.\\
Sons of Aaron, \textbf{trust} in \textbf{the} Lord; *\\
he is their \textbf{help} and \textbf{their} shield.

You who fear him, \textbf{trust} in \textbf{the} Lord; *\\
he is their \textbf{help} and \textbf{their} shield.\\
He remembers us, and he will bless us; †\\
he will bless the \textbf{sons} of \textbf{Is}-ra-el. *\\
He will bless the \textbf{sons} of \textbf{Aa}ron.

The Lord will bless \textbf{those} who \textbf{fear} him, *\\
the little no \textbf{less} than \textbf{the} great:\\
to you may the \textbf{Lord} grant \textbf{in}crease, *\\
to you and \textbf{all} your \textbf{child}ren.

May you be \textbf{blessed} by \textbf{the} Lord, *\\
the maker of \textbf{hea}ven \textbf{and} earth.\\
The heavens be\textbf{long} to \textbf{the} Lord *\\
but the earth he has \textbf{giv}en \textbf{to} men.\\

The dead shall \textbf{not} praise \textbf{the} Lord, *\\
nor those who go down in\textbf{to} the \textbf{sil}ence.\\
But we who \textbf{live} bless \textbf{the} Lord *\\
now and for \textbf{ev}er. \textbf{Am}en.

