%Not to us, Lord, not to us, *\\
%but to your name give the glory\\
for the sake of \emph{your} \textbf{love} and your truth, *\\
lest the heathen say: “Where \emph{is} \textbf{their} God?”

But our God \emph{is} \textbf{in} the heavens; *\\
he does whatev\emph{er} \textbf{he} wills.\\
Their idols \emph{are} \textbf{sil}ver and gold, *\\
the work of \emph{hu}\textbf{man} hands.

They have mouths \emph{but} \textbf{they} cannot speak; *\\
they have eyes but they \emph{can}\textbf{not} see;\\
they have ears \emph{but} \textbf{they} cannot hear; *\\
they have nostrils but they \emph{can}\textbf{not} smell.

With their hands they cannot feel; †\\
with their \emph{feet} \textbf{they} cannot walk. *\\
No sound comes \emph{from} \textbf{their} throats.\\
Their makers will \emph{come} \textbf{to} be like them *\\
and so will all who \emph{trust} \textbf{in} them.

Sons of Is\emph{rael}, \textbf{trust} in the Lord; *\\
he is their help \emph{and} \textbf{their} shield.\\
Sons of Aa\emph{ron}, \textbf{trust} in the Lord; *\\
he is their help \emph{and} \textbf{their} shield.

You who fear \emph{him}, \textbf{trust} in the Lord; *\\
he is their help \emph{and} \textbf{their} shield.\\
He remembers us, and he will bless us; †\\
he will bless \emph{the} \textbf{sons} of Israel. *\\
He will bless the sons \emph{of} \textbf{Aar}on.

The Lord will \emph{bless} \textbf{those} who fear him, *\\
the little no less \emph{than} \textbf{the} great:\\
to you may \emph{the} \textbf{Lord} grant increase, *\\
to you and all \emph{your} \textbf{child}ren.

May you \emph{be} \textbf{blessed} by the Lord, *\\
the maker of hea\emph{ven} \textbf{and} earth.\\
The heavens \emph{be}\textbf{long} to the Lord *\\
but the earth he has gi\emph{ven} \textbf{to} men.\\

The dead \emph{shall} \textbf{not} praise the Lord, *\\
nor those who go down into \emph{the} \textbf{sil}ence.\\
But we \emph{who} \textbf{live} bless the Lord *\\
now and for \emph{ever}. \textbf{A}men.

