% !TEX root = 8-OT-C-VII.tex
% !TEX recipe = LuaLaTeX+se
%\documentclass{article}
\documentclass[paper=letter,parskip]{scrartcl} % set document class: manual at https://ctan.org/pkg/koma-script
%\usepackage{fontspec}

% Load packages:
\usepackage[osf,p]{libertine} % set font
\usepackage[autocompile]{gregoriotex} % enable Gregorio score inclusion
\usepackage[latin]{babel} % set language
\usepackage{multicol}
\usepackage[margin=2cm]{geometry}
\usepackage{scrlayer-scrpage}
\usepackage{xargs}

\newcommand{\myhome}{C:/Users/johna/Chant/}
\gresetgregpath{{\myhome}}

\setkomafont{section}{\normalfont\centering\huge\scshape\bfseries} % section heading style
\setkomafont{subsection}{\normalfont\centering\Large\scshape} % section heading style
\setkomafont{subsubsection}{\normalfont\centering\small\scshape} % section heading style
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\setkomafont{pagehead}{\scshape}
%\automark[section]{section}
%\automark*[subsection]{subsection}

%spacing before and after headers
\RedeclareSectionCommand[
  %runin=false,
  afterindent=false,
  beforeskip=.25\baselineskip,
  afterskip=.15\baselineskip]{subsubsection}
\RedeclareSectionCommand[
%runin=false,
    afterindent=false,
    beforeskip=.15\baselineskip,
    afterskip=.05\baselineskip]{subsection}
\RedeclareSectionCommand[
    %runin=false,
    afterindent=false,
    beforeskip=.25\baselineskip,
    afterskip=.15\baselineskip]{section}
\RedeclareSectionCommand[
    runin=false,
    afterindent=false,
    beforeskip=3.25ex plus 1ex minus .2ex,
    afterskip=3pt]{paragraph}
%\lohead[\thesection]
%{\thesection}
%\rohead[\thesubsection]
%{\thesubsection}
%\pagestyle{scrheadings}

\usepackage{soul}
\sethlcolor{white}
\let\oldhl\hl
\renewcommand{\hl}[1]{\ifchoir \oldhl{#1} \else #1 \fi}


\newif\iflect
\lectfalse

\newif\ifchoir
\choirfalse

\iflect\choirtrue\fi


% Set the space around the initial:
% See http://gregorio-project.github.io/gregoriotex/details.html for more details and options
\grechangedim{beforeinitialshift}{2.2mm}{scalable}
\grechangedim{afterinitialshift}{2.2mm}{scalable}
 
% Set the initial font (change 43 for a larger size):
%\grechangestyle{initial}{\fontsize{43}{43}\selectfont}%

% Make staff lines red; remove for black:
%\gresetlinecolor{gregoriocolor}

% Use the "commentary" field of the score in the top right corner:
\gresetheadercapture{commentary}{grecommentary}{string}
\grechangedim{commentaryseparation}{0.15mm}{scalable}

% Format annotation above initial
\grechangestyle{annotation}{\small\bfseries}


\newcommand{\hymn}[3]{
\subsubsection*{Hymn: ``#2'' \hfill
{\small\itshape #3}}
\ifchoir
\gregorioscore{hymns/#1/english.gabc}
\else
\gregorioscore{hymns/#1/english_v1.gabc}
    \begin{multicols}{2}
        \small
        \input{\myhome/hymns/#1/verses.tex}
\end{multicols}
\fi}

\newcommand{\introd}[1]{
    \subsection{Introduction}
    \marginpar{\small\scshape Stand}
    \ifchoir
    \gregorioscore{Communes/deus-in-adjutorium/#1}
    \else
    \begin{center}
        \emph{Oh God, come to my assistance. --\textbf{LORD, make haste to help me.}\\
        Glory be to the Father, and to the Son, and to the Holy Spirit.
        --\textbf{As it was in the beginning, is now, and ever shall be, world with out end. Amen. Alleluia.}}
        %\greseparator{3}{30}
    \end{center}
    \fi
}

\newcommandx{\psalm}[5][5=solesmes]{
    \gregorioscore{Antiphona/#1/#5.gabc}
    \gresetinitiallines{0}
    \ifchoir
    \gregorioscore{Psalms/#2/#3.gabc}
    \begin{multicols}{2}
        \small
        \input{\myhome/Psalms/#2/#4.tex}

        \input{\myhome/Psalms/GloriaPatri/#4.tex}
    \end{multicols}
    \else
    \begin{multicols}{2}
        \small
        \input{\myhome/Psalms/#2/all.tex}
    \end{multicols}
    \fi
    \gregorioscore{Antiphona/#1/english.gabc}
    \gresetinitiallines{1}
}

\newcommandx{\responsory}[2][2=english]{
    \subsubsection{Responsory}
    \ifchoir
\gregorioscore{Resp-breve/#1/#2-extended.gtex}
\else
\gregorioscore{Resp-breve/#1/#2.gtex}
\fi
}

\begin{document}

\thispagestyle{plain}
\section{Fifth Sunday of Lent 2025 at Second Vespers \iflect LECTIONARY \else\ifchoir CHOIR\fi\fi}
\iflect
\else
\ifchoir
\else
%\begin{center}
%    \emph{Feast of the Presentation of the Lord}
    %\emph{Prepared by Dr. J. Costanzo}
    %
    %    \greseparator{3}{30}
%\end{center}
%\vspace{-0.5cm}
\fi
\fi

\introd{festivus-lent}

\hymn{audi-benigne-conditor}{Audi, benigne Conditor}{Attributed to Saint Gregory the Great, ca. 540-604, © 2023 ICEL}

\vspace{-15pt}
\subsection{Psalmody}
\marginpar{\small\scshape Sit}
%% FIRST PSALM %%
\paragraph{Psalm 110[109]}
\greannotation{Ant. 1}
\greannotation{1f}
%\grecommentary{Ps. 110}
\psalm{sicut-exaltatus}{110}{1f}{2-0-1-2}

%% SECOND PSALM %%
\paragraph{Psalm 114[113]}
\greannotation{Ant. 2}
\greannotation{8c}
%\grecommentary{Ps. 130}
\psalm{ego-qui-loquor}{114}{8c}{1-0-1-2}


%% NT CANTICLE %%
\paragraph{Canticle: 1 Peter 2:21-24}
\greannotation{Ant. 3}
\greannotation{5a}
%\grecommentary{1 Peter 2:21-24}
\psalm{vulneratus-est}{1Pet2-21}{5a}{1-0-2-0}[verona]
% \paragraph{Canticle: Wedding Feast of the Lamb}
% \emph{In Ordinary Time, the Antiphonale Romanum
% provides no antiphon for this Canticle when the Office is sung.}
% \ifchoir
% \greannotation{Cant.}
% \greannotation{6}
% \gregorioscore{Canticum/salus-et-gloria/english-VI}
% \else
% \begin{multicols}{2}
%     \input{Canticum/salus-et-gloria/text.tex}    
% \end{multicols}
% \fi

\subsection{Reading: Acts 13:26-30}
\iflect
\gresetinitiallines{0}
\gabcsnippet{
    (c3) My(h) broth(h)ers,(h) it(h) was(h) to(h) us(h) that(h) this(h) mes(h)sage(h) of(h) sal(h)va(h)tion(h) was(h) sent(h) forth.(d.) (:) The(h) in(h)hab(h)it(h)ants(h) of(h) Je(h)ru(h)sa(h)lem(h) and(h) their(h) rul(h)ers(h) failed(h) to(h) rec(h)og(g)nize(f) him,(h.) (;) and(h) in(h) con(h)demn(h)ing(h) him(h) they(h) ful(h)filled(h) the(h) words(h) of(h) the(h) proph(h)ets(h) which(h) we(h) read(h) sab(h)bath(h) af(h)ter(h) sab(h)bath.(d.) (:) E(h)ven(h) though(h) they(h) found(h) no(h) charge(h) a(h)gainst(h) him(h) which(h) de(g)served(f) death,(h.) (;) they(h) begged(h) Pi(h)late(h) to(h) have(h) him(h) ex(h)e(h)cut(h)ed.(d.) (:) Once(h) they(h) had(h) brought(h) a(h)bout(h) all(h) that(h) had(h) been(h) writ(h)ten(g) of(f) him,(h.) (;) they(h) took(h) him(h) down(h) from(h) the(h) tree(h) and(h) laid(h) him(h) in(h) a(h) tomb.(d.) (:) Yet(h) God(h) raised(h) him(h) from(h) the(f) dead.(ef..) (::)
}
\gresetinitiallines{1}
\else
My brothers, it was to us that this message of salvation was sent forth. The inhabitants of Jerusalem and their rulers failed to recognize him, and in condemning him they fulfilled the words of the prophets which we read sabbath after sabbath. Even though they found no charge against him which deserved death, they begged Pilate to have him executed. Once they had brought about all that had been written of him, they took him down from the tree and laid him in a tomb. Yet God raised him from the dead.
\fi

\greannotation{Resp.}
\greannotation{2}
\responsory{ego-dixi-domine}[solesmes_1957]


\subsection{Gospel Canticle}
\marginpar{\small\scshape Stand}
\grechangedim{commentaryraise}{3.5mm}{scalable}
\greannotation{Ant.}
\greannotation{3a}
\psalm{nemo-te-condemnavit}{Magnificat}{3a}{2-0-2-0}[verona]

\subsection{Intercessions}
\gresetinitiallines{0}
% \iflect
% \gabcsnippet{
%     (c4)Re(f)joi(gh)cing(h) in(h) the(h) Lord,(h) from(h) whom(h) all(h)
%     good(g) things(ixi) come,(h)
%     — let(g) us(f) pray:(g.)
% }
% \fi
\ifchoir\emph{Recto tono.}
% \gabcsnippet{
%     (c4)Lord,(g) hear(g) our(h) prayer.(f.)
% }
\fi
\begin{multicols}{2}
    \small
%\iflect\else
All praise to God the Father who brought his chosen people 
to rebirth from imperishable seed through his eternal Word.\\
— Let us ask him as his children:\\
\textbf{Lord, be gracious to your people.}%\fi

God of mercy, hear the prayers we offer for all your people,\\
— may they hunger for your word more than for bodily food.\\
\textbf{Lord, be gracious to your people.}

Give us a sincere and active love for our own nation and for all mankind,
— may we work always to build a world of peace and goodness.\\
\textbf{Lord, be gracious to your people.}

Look with love on all to be reborn in baptism,\\
— that they may be living stones in your temple of the Spirit.\\
\textbf{Lord, be gracious to your people.}

You moved Nineveh to repentance by the preaching of Jonah,\\
— in your mercy touch the hearts of sinners by the preaching of your word.\\
\textbf{Lord, be gracious to your people.}

May the dying go in hope to meet Christ their judge,\\
— may they rejoice for ever in the vision of your glory.\\
\textbf{Lord, be gracious to your people.}
\end{multicols}

\subsubsection{Our Father}
\gresetinitiallines{0}
\gregorioscore{Communes/pater-noster/English-C}
\gresetinitiallines{1}

\subsubsection{Prayer \& Dismissal}
\iflect
\gabcsnippet{
    (c3) By(h) your(h) help,(h) we(h) be(h)seech(h) you,(h) Lord(g) our(f) God,(h.) (;) may(h) we(h) walk(h) ea(h)ger(h)ly(h) in(h) that(h) same(h) char(h)i(h)ty(h)
    with(h) which,(h) out(h) of(h) love(h) for(g) the(f) world,(h.) (;) your(h) Son(h) hand(h)ed(h) him(h)self(h) o(h)ver(h) to(h) death.(d.) (:) Through(h) our(h) Lord(h) Je(h)sus(h) Christ,(g) your(f) Son,(h.) (;) who(h) lives(h) and(h) reigns(h) with(h) you(h) in(h) the(h) u(h)ni(h)ty(h) of(h) the(h) Ho(g)ly(f) Spir(h)it,(h.) (;) God(h) for(h) ev(h)er(h) and(h) ev(h)er.(f.) (::) —A(h)men.(h.) (::)
    }
\else
By your help, we beseech you, Lord our God,
may we walk eagerly in that same charity
with which, out of love for the world,
your Son handed himself over to death.
Through our Lord Jesus Christ, your Son,
who lives and reigns with you in the unity of the Holy Spirit,
God for ever and ever.
— \textbf{Amen}.\fi

%%\begin{multicols}{2}
%%    \small
%%\emph{If a priest or deacon presides:}\\
%%The Lord be with you.\\
%%— \textbf{And with your spirit.}\\
%%May almighty God bless you,\\
%%the Father, and the Son, and the Holy Spirit.\\
%%— \textbf{Amen}.\\
%%Go in peace.\\
%%— \textbf{Thanks be to God.}
%%
%%\columnbreak
%%
%%\emph{In the absence of a priest or deacon and in individual recitation, Evening Prayer concludes:}
\iflect
%\input{C:/Users/johna/Chant/Communes/dominus-nos-benedicat/english-solemn.gtex}
\gabcsnippet{(c3) May(h) the(h) LORD(g) bless(f) us,(h.) (;) pro(h)tect(h) us(h) from(g) all(f) e(h)vil,(h.) (;) and(h) bring(h) us(h) to(h) ev(h)er(h)last(h)ing(h) life.(f.) (::)}
\fi

\begin{center}
    \iflect
    %\gabcsnippet{
    %    (c3) May(h) the(h) lord(g) bless(f) us,(h.) (;) pro(h)tect(h) us(h) from(g) all(f) e(h)vil,(h.) (;) and(h) bring(h) us(h) to(h) ev(h)er(h)last(h)ing(f) life.(f.) (:) —A(g.)men.(h.) (::)
    %}
    \else
    May the Lord + bless us, %\\
protect us from all evil %\\
and bring us to everlasting life.
— \textbf{Amen}.\\
\fi

\emph{The Antiphon Ave Regina Cælorum
    to the Blessed Virgin Mary is traditionlly sung at Night Prayer
    (Compline) from February 2nd
    until the beginning of the Easter Season.}
\end{center}

\gregorioscore{hymns/ave-regina-caelorum/solesmes.gabc}

\end{document}