%& -output-directory=C:\Users\johna\Dropbox\Chants\ -aux-directory=.\temp
% !TEX recipe = LuaLaTeX+se
%\documentclass{article}
\documentclass[10pt,parskip,paper=216mm:162mm,DIV=calc]{scrartcl} % set document class: manual at https://ctan.org/pkg/koma-script
%\usepackage{fontspec}

% Load packages:
\usepackage[osf,p]{libertine} % set font
\usepackage[autocompile]{gregoriotex} % enable Gregorio score inclusion
\usepackage[latin]{babel} % set language
\usepackage{multicol}
\usepackage[margin=1cm]{geometry}
\usepackage{scrlayer-scrpage}
\usepackage{hyperref}
%\usepackage{musixtex}

\newcommand{\myhome}{C:/Users/johna/Chant/}
\gresetgregpath{{\myhome}}

\setkomafont{section}{\normalfont\centering\huge\scshape} % section heading style
\setkomafont{subsection}{\normalfont\centering\Large\bfseries} % section heading style
\setkomafont{subsubsection}{\normalfont\centering\small\scshape} % section heading style
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\setkomafont{pagehead}{\scshape}
\automark[section]{section}
\automark*[subsection]{subsection}

%\lohead[\thesubsection]
%{\thesubsection}
%\rohead[\thesubsection]
%{\thesubsection}
\pagestyle{scrheadings}

\RedeclareSectionCommand[
    runin=true,
    afterindent=false,
    beforeskip=0.75ex plus 1ex minus .2ex,
    afterskip=3pt]{paragraph}

% Set the space around the initial:
% See http://gregorio-project.github.io/gregoriotex/details.html for more details and options
\grechangedim{beforeinitialshift}{2.2mm}{scalable}
\grechangedim{afterinitialshift}{2.2mm}{scalable}

% Set the initial font (change 43 for a larger size):
%\grechangestyle{initial}{\fontsize{43}{43}\selectfont}%

% Make staff lines red; remove for black:
%\gresetlinecolor{gregoriocolor}

% Use the "commentary" field of the score in the top right corner:
\gresetheadercapture{commentary}{grecommentary}{string}
\grechangedim{commentaryraise}{3.5mm}{scalable}

% Format annotation above initial
\grechangestyle{annotation}{\small\bfseries}

\begin{document}
\subsection{Sept 29 - Archangels Michael, Gabriel, and Raphael}

Sept 29
In: Bless the Lord, all you his angels, mighty in power,
fulfilling his word and heeding his voice.

Resp: In the sight of the angels I will sing your praises, Lord.
In conspéctu angelórum psallam tibi, Dómine.

Al: Bless the Lord, all you his angels,
his ministers who do his will.
Benedícite Dómino, omnes virtútes eius,
minístri eius, qui fácitis voluntátem eius.

Of: The Angel stood at the altar of the temple with a golden censer
in his hand; and he was given much incense and the smoke of the
incense ascended before the presence of God, alleluia.

Co: I will thank you Lord, with all my heart;
in the presence of the Angels I will praise you.
Confitébor tibi, Dómine, in toto corde meo,
in conspéctu Angelórum psallam tibi.



Oct 2

In: Angels of the Lord, bless the Lord,
praise and exalt him above all for ever.
Benedícite, omnes Angeli Dómini, Dóminum,
hymnum dícite, et superexaltáte eum in sǽcula.

Resp: The Lord has put his angels in charge of you, to guard you in all your ways.
Angelis suis mandábit de te,
ut custódiant te in ómnibus viis tuis.

Al: Bless the LORD, all you angels,
you ministers, who do his will.
Benedícite Dómino, omnes virtútes eius,
minístri eius, qui fácitis voluntátem eius.

Of: The Angel of the Lord shall encamp round about those who
fear him and shall deliver them; taste and see how good the Lord
is.

Co: In the presence of the Angels I will praise you, my God.
In conspéctu Angelórum psallam tibi, Deus meus.



\filbreak
%\greannotation{In. I}
\phantomsection
\gregorioscore{Introitus/benedicite-dominum/english.gabc}~\label{in:benedicite-dominum}

\filbreak
%\greannotation{In. I}
\phantomsection
\gregorioscore{Alleluia/sancte-michael/solesmes.gabc}~\label{al:sancte-michael}
Or: Benedicite Domino,~\pageref{al:benedicite-domino}.

\filbreak
\phantomsection
\gregorioscore{Offertorium/stetit-angelus/english.gabc}~\label{of:stetit-angelus}


\filbreak
%\greannotation{Co. III}
\phantomsection
\gregorioscore{Communio/benedicite-omnes-angeli/english.gabc}~\label{co:benedicite-omnes-angeli}



\subsubsection{Oct 2 - Holy Guardian Angels}

\textbf{Introit}---Graduale option: Benedicite Dominum,~\pageref{in:benedicite-dominum};
Missal option: the \textbf{Communion} chant
Benedicite omnes Angeli,~\pageref{co:benedicite-omnes-angeli}.

\filbreak
%\greannotation{In. I}
\phantomsection
\gregorioscore{Alleluia/benedicite-domino/english.gabc}~\label{al:benedicite-domino}

\filbreak
\gregorioscore{Offertorium/immittet-angelus/english.gabc}

\textbf{Communion}---Graduale option: Benedicite omnes Angeli,~\pageref{co:benedicite-omnes-angeli};
Missal option:
\gregorioscore{Antiphona/in-conspectu-angelorum/english.gabc}

\end{document}