%& -output-directory=C:\Users\johna\Dropbox\Chants\ -aux-directory=.\temp
% !TEX recipe = LuaLaTeX+se
%\documentclass{article}
\documentclass[10pt,parskip,paper=216mm:162mm,DIV=calc]{scrartcl} % set document class: manual at https://ctan.org/pkg/koma-script
%\usepackage{fontspec}

% Load packages:
\usepackage[osf,p]{libertine} % set font
\usepackage[autocompile]{gregoriotex} % enable Gregorio score inclusion
\usepackage[latin]{babel} % set language
\usepackage{multicol}
\usepackage[margin=1cm]{geometry}
\usepackage{scrlayer-scrpage}
%\usepackage{musixtex}

\newcommand{\myhome}{C:/Users/johna/Chant/}
\gresetgregpath{{\myhome}}

\setkomafont{section}{\normalfont\centering\huge\scshape} % section heading style
\setkomafont{subsection}{\normalfont\centering\Large\bfseries} % section heading style
\setkomafont{subsubsection}{\normalfont\centering\small\scshape} % section heading style
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\setkomafont{pagehead}{\scshape}
\automark[section]{section}
\automark*[subsection]{subsection}

%\lohead[\thesubsection]
%{\thesubsection}
%\rohead[\thesubsection]
%{\thesubsection}
\pagestyle{scrheadings}

\RedeclareSectionCommand[
    runin=true,
    afterindent=false,
    beforeskip=0.75ex plus 1ex minus .2ex,
    afterskip=3pt]{paragraph}

% Set the space around the initial:
% See http://gregorio-project.github.io/gregoriotex/details.html for more details and options
\grechangedim{beforeinitialshift}{2.2mm}{scalable}
\grechangedim{afterinitialshift}{2.2mm}{scalable}

% Set the initial font (change 43 for a larger size):
%\grechangestyle{initial}{\fontsize{43}{43}\selectfont}%

% Make staff lines red; remove for black:
%\gresetlinecolor{gregoriocolor}

% Use the "commentary" field of the score in the top right corner:
\gresetheadercapture{commentary}{grecommentary}{string}

% Format annotation above initial
\grechangestyle{annotation}{\small\bfseries}

\begin{document}
\subsection{July 3 - Feast of St. Thomas, Apostle}

\begin{multicols}{2}
   \paragraph{Entrance Antiphon}~\emph{Cf. Ps 118 (117): 28, 21}
   \small
   You are my God, and I confess you;
   you are my God, and I exalt you;
   I will thank you, for you became my savior.

   \columnbreak

   \paragraph{Introit}~\emph{Cf. Ps 139 (138): 17}
   To me, Your friends, O God, are made exceedingly honorable;
   their principality is exceedingly strengthened.
   
\end{multicols}

\begin{multicols}{2}
   \small
   \paragraph{Resp. Psalm}~
   \emph{Ps 117:1bc, 2}\\
   \textbf{(Mk 16:15) Go out to all the world and tell the Good News.}\\
   Praise the LORD, all you nations;\\
   glorify him, all you peoples! \Rbar

   For steadfast is his kindness for us,\\
   and the fidelity of the LORD endures forever.

   \columnbreak

   \paragraph{Gradual}~
   \textbf{Nimis honorati sunt}\\
   \emph{Ps. 139 (138): 17-18} Your friends, O God, are made
   exceedingly honorable: their principality is exceedingly strengthened.
   \Vbar Were I to recount them, they would outnumber the sands.
   
\end{multicols}


\begin{multicols}{2}
   \paragraph{Alleluia}~\emph{John 20:29}
   \small
   You believe in me, Thomas, because you have seen me, says the Lord;
   blessed are those who have not seen, but still believe!

   \columnbreak

   \paragraph{\emph{Graduale}}~\emph{Ps. 33 (32): 1} Exult, you just, in the Lord;
   praise from the upright is fitting. \\
   \emph{Revised Grail:}
   Ring out your joy to the Lord, O you just;  for praise is fitting from the upright.  

      
\end{multicols}

\paragraph{Offertory Chant} \emph{Ps 19 (18):5}
Through all the earth their voice resounds, and to the ends of the world, their message.\\
\emph{Revised Grail:} Their sound goes forth through all the earth,  their message to the utmost bounds of the world.  


\paragraph{Communion Antiphon/Chant} \emph{Jn. 20:27}
Bring your hand and feel the place of the nails,
and do not be unbelieving but believing.

% \begin{multicols}{3}
%    \paragraph{Communion chants}~\\
%    \small
%     {\bfseries Circuibo}\\
%     \emph{Ps. 26:6}
%     I shall offer within his tent
%    sacrifices full of exultation.
%    I will sing and make music for the Lord. 
%    \columnbreak

%    {\bfseries Quod dico vobis}
%    \emph{Sun. Year A}\\
%    \emph{Mt. 10:27}
%    What I say to you in the darkness, speak in the light, says the Lord.
%    What you hear whispered, proclaim on the housetops.
%    \columnbreak

%    {\bfseries Qui vult venire}
%    \emph{Sun. Year C}\\
%    \emph{Mt 16:24}
%    Whoever wishes to come after me, must deny himself,
%    take up his cross, and follow me.
% \end{multicols}

\filbreak
\greannotation{In. II}
\gregorioscore{Introitus/mihi-autem-nimis/english-ant-only.gabc}
\gresetinitiallines{0}
\gabcsnippet{
   (f3)You(e) are(fe) my(eh) God,(h) and(h) I(h) con(h)fess(h) you; †(h.) you(h) are(h) my(h) God,(h) <i>and</i>(hg) <i>I</i>(hi) <i>ex</i>(i)<b>alt</b>(hi) you;(h.) * (:) I(hf) will(fh) thank(h) you,(h) for(h) you(h) <i>be</i>(i)<i>came</i>(hf) <i>my</i>(h) <i>sa</i>(ge)<i>vior</i>.(fgf.) (::)
}
\gresetinitiallines{1}

\filbreak
\greannotation{Of. II}
\gregorioscore{Offertorium/in-omnem-terram/english.gabc}

\filbreak
\greannotation{Co. VI}
\gregorioscore{Communio/mitte-manum/english.gabc}
% \gresetinitiallines{0}
% \gabcsnippet{
% }
% \gresetinitiallines{1}


\end{document}